\chapter*{List of Publications/Conferences} % Publications page text
\markboth{}{}
\fontsize{11pt}{12pt} \selectfont
%\section*{CMS Public Notes with Direct Contribution}  % Here
%\section*{CMS Public Documents}% : Physics Analysis Summary}
\begin{itemize}
{\Large \item {\bf ~CMS Public Documents}}
\begin{enumerate}

\item CMS Collaboration,``Determination of the strong coupling constant from the measurement of inclusive multijet event cross sections in pp collisions at $\sqrt{s} = 8~\mathrm{TeV}$'', {\bf CMS-PAS-SMP-16-008} (2017).

\end{enumerate}

\vspace*{3mm}
%\noindent\makebox[\textwidth]{\rule{\textwidth}{1pt}} 

%\section*{CMS Analysis Notes with Direct Contribution}  % Here  
%\section*{CMS Internal Documents}
{\Large \item {\bf ~CMS Internal Documents}}
\begin{itemize}
\item {\large \bf Analysis Notes} 
\begin{enumerate}

\item A. Kaur {\it et al.}, ``Search for light scalar resonances decaying to b quarks at $\sqrt{s}$ = 13 TeV'', {\bf CMS AN-2016/384} (2016).

\item A. Kaur {\it et al.}, ``Measurement of inclusive multijet cross-sections in pp collisions at $\sqrt{s}$ = 8 TeV'', {\bf CMS AN-2015/102} (2015).

\end{enumerate}
\vspace*{2mm}
\item {\large \bf Detector Note} 
\begin{enumerate}

\item A. Kaur {\it et al.}, ``Commissioning and performance of the CMS Hadron Outer Calorimeter'', {\bf CMS DN-14-019} (2014).

\end{enumerate}
\end{itemize}
\vspace*{3mm}
%\noindent\makebox[\textwidth]{\rule{\textwidth}{1pt}} % Here

%\section*{Papers in Refreed Journals}
{\Large \item {\bf ~Papers in Refreed Journals}}
\begin{enumerate}

\item A. Kaur {\it et al.}, ``Measurements of event properties and multi-differential jet cross sections and impact of CMS measurements on Proton Structure and QCD parameters'', EPJ Web of Conferences {\bf 172} (2018) doi:\href{https://doi.org/10.1051/epjconf/201817202001}{10.1051/epjconf/201817202001}.

\item A. Kaur {\it et al.}, ``Extraction of the strong coupling constant from the measurement of inclusive multijet event cross-sections in pp collisions at center of mass energy of 8 TeV'', Springer Proc. Phys. {\bf 203}, 02001 (2018) doi:10.1007/978-3-319-73171-1.

\item M. Kaur and Anter P. Kaur, ``Subjet Multiplicities at LHC Energies and the QCD Color Factor Ratio C$_{A}$/C$_{F}$'', Advances in High Energy Physics {\bf 2013}, Article ID 585809 (2013) doi:10.1155/2013/585809.
\
\end{enumerate}
\vspace*{3mm}
%\noindent\makebox[\textwidth]{\rule{\textwidth}{1pt}} 

%\section*{Papers presented in Conferences, Workshops and Symposiums}
{\Large \item {\bf ~Papers presented in Conferences, Workshops and Symposiums}}
\begin{enumerate}
\item A. Kaur {\it et al.}, ``Measurements of event properties and multi-differential jet cross sections and impact of CMS measurements on Proton Structure and QCD parameters'', {\bf XLVII International Symposium on Multiparticle Dynamics (ISMD2017)}, 11-15 September, 2017, Tlaxcala City, Mexico.

\item A. Kaur {\it et al.}, ``Measurement of inclusive multijet cross sections in pp collisions using the CMS detector'', {\bf 11$^{\rm \it th}$ Chandigarh Science Congress, CHASCON 2017}, 9-11 March, 2017, Panjab University, Chandigarh, India.  

\item A. Kaur {\it et al.}, ``Extraction of the strong coupling constant from the measurement of inclusive multijet event cross-sections in pp collisions at center of mass energy of 8 TeV'', {\bf XXII DAE­-BRNS High Energy Physics Symposium 2016}, 12-16 December, 2016, Delhi, India.

\item A. Kaur {\it et al.}, ``Inclusive jets results from CMS'', {\bf International Workshop on Frontiers in Electroweak Interactions of Leptons and Hadrons}, 2-6 November, 2016, Aligarh, India.

\item A. Kaur {\it et al.}, ``HCAL Back-end Upgradation at CMS Detector'', {\bf 9$^{\rm \it th}$ Chandigarh Science Congress, CHASCON 2015}, 25-27 February, 2015, Panjab University, Chandigarh, India.

\end{enumerate}
\vspace*{3mm}
%\noindent\makebox[\textwidth]{\rule{\textwidth}{1pt}} 

%\section*{Conferences, Schools and Workshops attended}
{\Large \item {\bf ~Conferences, Schools and Workshops attended}}
\begin{enumerate}

\item {\bf Workshop on Upgrade of the CMS Calorimeter}, 23-24 November, 2015, Tata Institute of Fundamental Research, Mumbai, India.

\item {\bf IX SERC SCHOOL ON EXPERIMENTAL HIGH ENERGY PHYSICS}, 2-21 December, 2013, Indian Institute of Technology Madras, Chennai, India. 

\item {\bf CMS Data Analysis School (CMSDAS)}, 7-11 November, 2013, Saha Institute of Nuclear Physics, Kolkata, India.

\item {\bf 5$^{\it th}$ Chandigarh Science Congress, CHASCON 2011}, 26-28 February, 2011, Panjab University, Chandigarh, India.
\end{enumerate}
\vspace*{3mm}
%\noindent\makebox[\textwidth]{\rule{\textwidth}{1pt}} 
%\inputencoding{latin2}
%\section*{CMS Publications}       % Here
%\section*{CMS Publications\protect\footnotemark}
{\Large \item {\bf ~CMS Publications\protect\footnotemark}}
\footnotetext{I am a co-author of more than 300 ``Journal Articles'' with the CMS Collaboration and the full list of publications can be found at \href{http://inspirehep.net/search?ln=en&as=1&m1=e&p1=Anterpreet+Kaur&f1=author&op1=a&m2=p&p2=&f2=collaboration&op2=a&m3=a&p3=&f3=&action_search=Search&sf=&so=d&rm=&rg=25&sc=0&of=hb}{http://inspirehep.net}.}
\begin{enumerate}
%\cite{Sirunyan:2017vkm}
%\bibitem{Sirunyan:2017vkm} 
\item CMS Collaboration, ``Search for heavy resonances decaying to a top quark and a bottom quark in the lepton+jets final state in proton-proton collisions at 13 TeV'', Phys.\ Lett.\ B {\bf 777}, 39 (2018).
  %doi:10.1016/j.physletb.2017.12.006
  %[arXiv:1708.08539 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.12.006;%%
  %2 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017qkz}
%\bibitem{Sirunyan:2017qkz} 
\item CMS Collaboration, ``Search for Evidence of the Type-III Seesaw Mechanism in Multilepton Final States in Proton-Proton Collisions at $\sqrt{s}=13\text{ }\text{ }\mathrm{TeV}$'', Phys.\ Rev.\ Lett.\  {\bf 119}, no. 22, 221802 (2017).
  %doi:10.1103/PhysRevLett.119.221802
  %[arXiv:1708.07962 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevLett.119.221802;%%
  %5 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017gyb}
%\bibitem{Sirunyan:2017gyb} 
\item CMS Collaboration, ``Principal-component analysis of two-particle azimuthal correlations in PbPb and $p\text{Pb}$ collisions at CMS'', Phys.\ Rev.\ C {\bf 96}, no. 6, 064902 (2017).
  %doi:10.1103/PhysRevC.96.064902
  %[arXiv:1708.07113 [nucl-ex]].
  %%CITATION = %doi:10.1103/PhysRevC.96.064902;%%
  %1 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017fvv}
%\bibitem{Sirunyan:2017fvv} 
\item CMS Collaboration, ``Measurement of vector boson scattering and constraints on anomalous quartic couplings from events with four leptons and two jets in proton-proton collisions at $\sqrt{s}=$ 13 TeV'', Phys.\ Lett.\ B {\bf 774}, 682 (2017).
  %doi:10.1016/j.physletb.2017.10.020
  %[arXiv:1708.02812 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.10.020;%%
  %2 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017uvf}
%\bibitem{Sirunyan:2017uvf} 
\item CMS Collaboration, ``Search for a light pseudoscalar Higgs boson produced in association with bottom quarks in pp collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1711}, 010 (2017).
  %doi:10.1007/JHEP11(2017)010
  %[arXiv:1707.07283 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP11(2017)010;%%
  %2 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017yse}
%\bibitem{Sirunyan:2017yse} 
\item CMS Collaboration, ``Search for supersymmetry in events with at least one photon, missing transverse momentum, and large transverse event activity in proton-proton collisions at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1712}, 142 (2017).
  %doi:10.1007/JHEP12(2017)142
  %[arXiv:1707.06193 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP12(2017)142;%%
  %6 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017wgx}
%\bibitem{Sirunyan:2017wgx} 
\item CMS Collaboration, ``Measurement of the differential cross sections for the associated production of a $W$ boson and jets in proton-proton collisions at $\sqrt{s}=13$ TeV'', Phys.\ Rev.\ D {\bf 96}, no. 7, 072005 (2017).
  %doi:10.1103/PhysRevD.96.072005
  %[arXiv:1707.05979 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevD.96.072005;%%
  %5 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017wif}
%\bibitem{Sirunyan:2017wif} 
\item CMS Collaboration, ``Search for direct production of supersymmetric partners of the top quark in the all-jets final state in proton-proton collisions at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1710}, 005 (2017).
  %doi:10.1007/JHEP10(2017)005
  %[arXiv:1707.03316 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP10(2017)005;%%
  %14 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017wto}
%\bibitem{Sirunyan:2017wto} 
\item CMS Collaboration, ``Search for heavy resonances that decay into a vector boson and a Higgs boson in hadronic final states at $\sqrt{s} = 13$ $\,\text {TeV}$'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 9, 636 (2017).
  %doi:10.1140/epjc/s10052-017-5192-z
  %[arXiv:1707.01303 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-5192-z;%%
  %13 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017tqd}
%\bibitem{Sirunyan:2017tqd} 
\item CMS Collaboration, ``Constraints on anomalous Higgs boson couplings using production and decay information in the four-lepton final state'', Phys.\ Lett.\ B {\bf 775}, 1 (2017).
  %doi:10.1016/j.physletb.2017.10.021
  %[arXiv:1707.00541 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.10.021;%%
  %5 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017tqo}
%\bibitem{Sirunyan:2017tqo} 
\item CMS Collaboration, ``Search for Higgs boson pair production in the $bb\tau\tau$ final state in proton-proton collisions at $\sqrt{(}s)=8\text{ }\text{ }\mathrm{TeV}$'', Phys.\ Rev.\ D {\bf 96}, no. 7, 072004 (2017).
  %doi:10.1103/PhysRevD.96.072004
  %[arXiv:1707.00350 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevD.96.072004;%%
  %8 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017zmn}
%\bibitem{Sirunyan:2017zmn} 
\item CMS Collaboration, ``Measurement of charged pion, kaon, and proton production in proton-proton collisions at $\sqrt{s}=13$ TeV'', Phys.\ Rev.\ D {\bf 96}, no. 11, 112003 (2017).
  %doi:10.1103/PhysRevD.96.112003
  %[arXiv:1706.10194 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevD.96.112003;%%
  %2 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017exp}
%\bibitem{Sirunyan:2017exp} 
\item CMS Collaboration, ``Measurements of properties of the Higgs boson decaying into the four-lepton final state in pp collisions at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1711}, 047 (2017).
  %doi:10.1007/JHEP11(2017)047
  %[arXiv:1706.09936 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP11(2017)047;%%
  %25 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017zss}
%\bibitem{Sirunyan:2017zss} 
\item CMS Collaboration, ``Search for electroweak production of charginos and neutralinos in WH events in proton-proton collisions at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1711}, 029 (2017).
  %doi:10.1007/JHEP11(2017)029
  %[arXiv:1706.09933 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP11(2017)029;%%
  %3 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017xnz}
%\bibitem{Sirunyan:2017xnz} 
\item CMS Collaboration, ``Search for a heavy composite Majorana neutrino in the final state with two leptons and two quarks at $\sqrt{s}=13$ TeV'', Phys.\ Lett.\ B {\bf 775}, 315 (2017).
  %doi:10.1016/j.physletb.2017.11.001
  %[arXiv:1706.08578 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.11.001;%%
  %7 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017iyh}
%\bibitem{Sirunyan:2017iyh} 
\item CMS Collaboration, ``Measurement of the semileptonic $ \mathrm{t}\overline{\mathrm{t}} $ + $\gamma$ production cross section in pp collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1710}, 006 (2017).
  %doi:10.1007/JHEP10(2017)006
  %[arXiv:1706.08128 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP10(2017)006;%%
  %4 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017tyr}
%\bibitem{Sirunyan:2017tyr} 
\item CMS Collaboration, ``Measurements of jet charge with dijet events in pp collisions at $\sqrt{s}$ = 8 TeV'', JHEP {\bf 1710}, 131 (2017).
  %doi:10.1007/JHEP10(2017)131
  %[arXiv:1706.05868 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP10(2017)131;%%

%\cite{Sirunyan:2017ulk}
%\bibitem{Sirunyan:2017ulk} 
\item CMS Collaboration, ``Particle-flow reconstruction and global event description with the CMS detector'', JINST {\bf 12}, no. 10, P10003 (2017).
  %doi:10.1088/1748-0221/12/10/P10003
  %[arXiv:1706.04965 [physics.ins-det]].
  %%CITATION = %doi:10.1088/1748-0221/12/10/P10003;%%
  %120 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017xse}
%\bibitem{Sirunyan:2017xse} 
\item CMS Collaboration, ``Search for top squark pair production in pp collisions at $ \sqrt{s}=13 $ TeV using single lepton events'', JHEP {\bf 1710}, 019 (2017).
  %doi:10.1007/JHEP10(2017)019
  %[arXiv:1706.04402 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP10(2017)019;%%
  %13 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017ukk}
%\bibitem{Sirunyan:2017ukk} 
\item CMS Collaboration, ``Searches for W' bosons decaying to a top quark and a bottom quark in proton-proton collisions at 13 TeV'', JHEP {\bf 1708}, 029 (2017).
  %doi:10.1007/JHEP08(2017)029
  %[arXiv:1706.04260 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP08(2017)029;%%
  %8 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017ewk}
%\bibitem{Sirunyan:2017ewk} 
\item CMS Collaboration, ``Search for new physics in the monophoton final state in proton-proton collisions at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1710}, 073 (2017).
  %doi:10.1007/JHEP10(2017)073
  %[arXiv:1706.03794 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP10(2017)073;%%
  %9 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017usq}
%\bibitem{Sirunyan:2017usq} 
\item CMS Collaboration, ``Search for pair production of vector-like T and B quarks in single-lepton final states using boosted jet substructure in proton-proton collisions at  $\sqrt{s}=13$ TeV'', JHEP {\bf 1711}, 085 (2017).
  %doi:10.1007/JHEP11(2017)085
  %[arXiv:1706.03408 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP11(2017)085;%%
  %10 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017xgm}
%\bibitem{Sirunyan:2017xgm} 
\item CMS Collaboration, ``Search for dark matter produced in association with heavy-flavor quark pairs in proton-proton collisions at $\sqrt{s}=13$ TeV'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 12, 845 (2017).
  %doi:10.1140/epjc/s10052-017-5317-4
  %[arXiv:1706.02581 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-5317-4;%%
  %15 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017jin}
%\bibitem{Sirunyan:2017jin} 
\item CMS Collaboration, ``Search for top quark partners with charge 5/3 in proton-proton collisions at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1708}, 073 (2017).
  %doi:10.1007/JHEP08(2017)073
  %[arXiv:1705.10967 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP08(2017)073;%%
  %4 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017dnz}
%\bibitem{Sirunyan:2017dnz} 
\item CMS Collaboration, ``Search for Low Mass Vector Resonances Decaying to Quark-Antiquark Pairs in Proton-Proton Collisions at $\sqrt{s}=13\text{ }\text{ }\mathrm{TeV}$'', Phys.\ Rev.\ Lett.\  {\bf 119}, no. 11, 111802 (2017).
  %doi:10.1103/PhysRevLett.119.111802
  %[arXiv:1705.10532 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevLett.119.111802;%%
  %9 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017snr}
%\bibitem{Sirunyan:2017snr} 
\item CMS Collaboration, ``Measurements of $t\bar{t}$ cross sections in association with $b$ jets and inclusive jets and their ratio using dilepton final states in pp collisions at $\sqrt{s}$ = 13 TeV'', Phys.\ Lett.\ B {\bf 776}, 355 (2018).
  %doi:10.1016/j.physletb.2017.11.043
  %[arXiv:1705.10141 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.11.043;%%
  %2 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017nrt}
%\bibitem{Sirunyan:2017nrt} 
\item CMS Collaboration, ``Combination of searches for heavy resonances decaying to WW, WZ, ZZ, WH, and ZH boson pairs in proton-proton collisions at $\sqrt{s}=8$ and 13 TeV'', Phys.\ Lett.\ B {\bf 774}, 533 (2017).
  %doi:10.1016/j.physletb.2017.09.083
  %[arXiv:1705.09171 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.09.083;%%
  %11 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017oug}
%\bibitem{Sirunyan:2017oug} 
\item CMS Collaboration, ``Measurement of the ${B}^{\pm}$ Meson Nuclear Modification Factor in Pb-Pb Collisions at $\sqrt{{s}_{NN}}=5.02\text{ }\text{ }\mathrm{TeV}$'', Phys.\ Rev.\ Lett.\  {\bf 119}, no. 15, 152301 (2017).
  %doi:10.1103/PhysRevLett.119.152301
  %[arXiv:1705.04727 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevLett.119.152301;%%
  %4 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017fsj}
%\bibitem{Sirunyan:2017fsj} 
\item CMS Collaboration, ``Search for Supersymmetry in $pp$ Collisions at $\sqrt{s}=13\text{ }\text{ }\mathrm{TeV}$ in the Single-Lepton Final State Using the Sum of Masses of Large-Radius Jets'', Phys.\ Rev.\ Lett.\  {\bf 119}, no. 15, 151802 (2017).
  %doi:10.1103/PhysRevLett.119.151802
  %[arXiv:1705.04673 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevLett.119.151802;%%
  %11 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017kqq}
%\bibitem{Sirunyan:2017kqq} 
\item CMS Collaboration, ``Search for new phenomena with the $M_{\mathrm {T2}}$ variable in the all-hadronic final state produced in proton-proton collisions at $\sqrt{s} = 13$ $\,\text {TeV}$'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 10, 710 (2017).
  %doi:10.1140/epjc/s10052-017-5267-x
  %[arXiv:1705.04650 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-5267-x;%%
  %24 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017sbn}
%\bibitem{Sirunyan:2017sbn} 
\item CMS Collaboration, ``Search for Charged Higgs Bosons Produced via Vector Boson Fusion and Decaying into a Pair of $W$ and $Z$ Bosons Using $pp$ Collisions at $\sqrt{s}=13\text{ }\text{ }\mathrm{TeV}$'', Phys.\ Rev.\ Lett.\  {\bf 119}, no. 14, 141802 (2017).
  %doi:10.1103/PhysRevLett.119.141802
  %[arXiv:1705.02942 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevLett.119.141802;%%
  %11 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017skj}
%\bibitem{Sirunyan:2017skj} 
\item CMS Collaboration, ``Measurement of the triple-differential dijet cross section in proton-proton collisions at $\sqrt{s}=8\,\text {TeV} $ and constraints on parton distribution functions'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 11, 746 (2017).
  %doi:10.1140/epjc/s10052-017-5286-7
  %[arXiv:1705.02628 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-5286-7;%%
  %7 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017anm}
%\bibitem{Sirunyan:2017anm} 
\item CMS Collaboration, ``Search for black holes in high-multiplicity final states in proton-proton collisions at $ \sqrt{s}=$13 TeV'', Phys.\ Lett.\ B {\bf 774}, 279 (2017).
  %doi:10.1016/j.physletb.2017.09.053
  %[arXiv:1705.01403 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.09.053;%%
  %7 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017cwe}
%\bibitem{Sirunyan:2017cwe} 
\item CMS Collaboration, ``Search for supersymmetry in multijet events with missing transverse momentum in proton-proton collisions at 13 TeV'', Phys.\ Rev.\ D {\bf 96}, no. 3, 032003 (2017).
  %doi:10.1103/PhysRevD.96.032003
  %[arXiv:1704.07781 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevD.96.032003;%%
  %38 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017uyt}
%\bibitem{Sirunyan:2017uyt} 
\item CMS Collaboration, ``Search for physics beyond the standard model in events with two leptons of same sign, missing transverse momentum, and jets in proton-proton collisions at $\sqrt{s} = 13\,\text {TeV} $'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 9, 578 (2017).
  %doi:10.1140/epjc/s10052-017-5079-z
  %[arXiv:1704.07323 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-5079-z;%%
  %15 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017idq}
%\bibitem{Sirunyan:2017idq} 
\item CMS Collaboration, ``Measurement of the top quark mass in the dileptonic $t\bar{t}$ decay channel using the mass observables $M_{b\ell}$, $M_{T2}$, and $M_{b\ell\nu}$ in pp collisions at $\sqrt{s}$=8 TeV'', Phys.\ Rev.\ D {\bf 96}, no. 3, 032002 (2017).
  %doi:10.1103/PhysRevD.96.032002
  %[arXiv:1704.06142 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevD.96.032002;%%
  %9 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017uhk}
%\bibitem{Sirunyan:2017uhk} 
\item CMS Collaboration, ``Search for $ \mathrm{t}\overline{\mathrm{t}} $ resonances in highly boosted lepton+jets and fully hadronic final states in proton-proton collisions at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1707}, 001 (2017).
  %doi:10.1007/JHEP07(2017)001
  %[arXiv:1704.03366 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP07(2017)001;%%
  %12 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017lvq}
%\bibitem{Sirunyan:2017lvq} 
\item CMS Collaboration, ``Measurements of the pp $\to W\gamma\gamma$ and pp $\to Z\gamma\gamma$ cross sections and limits on anomalous quartic gauge couplings at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1710}, 072 (2017).
  %doi:10.1007/JHEP10(2017)072
  %[arXiv:1704.00366 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP10(2017)072;%%
  %5 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017ygf}
%\bibitem{Sirunyan:2017ygf} 
\item CMS Collaboration, ``Search for new physics with dijet angular distributions in proton-proton collisions at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1707}, 013 (2017).
  %doi:10.1007/JHEP07(2017)013
  %[arXiv:1703.09986 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP07(2017)013;%%
  %8 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017bfa}
%\bibitem{Sirunyan:2017bfa} 
\item CMS Collaboration, ``Search for a heavy resonance decaying to a top quark and a vector-like top quark at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1709}, 053 (2017).
  %doi:10.1007/JHEP09(2017)053
  %[arXiv:1703.06352 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP09(2017)053;%%
  %6 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017yar}
%\bibitem{Sirunyan:2017yar} 
\item CMS Collaboration, ``Measurement of the jet mass in highly boosted ${\mathrm{t}}\overline{\mathrm{t}}$ events from pp collisions at $\sqrt{s}=8$ $\,\text {TeV}$'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 7, 467 (2017).
  %doi:10.1140/epjc/s10052-017-5030-3
  %[arXiv:1703.06330 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-5030-3;%%
  %6 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017bey}
%\bibitem{Sirunyan:2017bey} 
\item CMS Collaboration, ``Search for anomalous couplings in boosted $\mathrm{ WW/WZ }\to\ell\nu\mathrm{ q \bar{q} }$ production in proton-proton collisions at $\sqrt{s} =$ 8 TeV'', Phys.\ Lett.\ B {\bf 772}, 21 (2017).
  %doi:10.1016/j.physletb.2017.06.009
  %[arXiv:1703.06095 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.06.009;%%
  %10 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017hnk}
%\bibitem{Sirunyan:2017hnk} 
\item CMS Collaboration, ``Search for associated production of dark matter with a Higgs boson decaying to $ \mathrm{b}\overline{\mathrm{b}} $ or $\gamma \gamma$ at $ \sqrt{s}=13$ TeV'', JHEP {\bf 1710}, 180 (2017).
  %doi:10.1007/JHEP10(2017)180
  %[arXiv:1703.05236 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP10(2017)180;%%
  %21 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017yrk}
%\bibitem{Sirunyan:2017yrk} 
\item CMS Collaboration, ``Search for third-generation scalar leptoquarks and heavy right-handed neutrinos in final states with two tau leptons and two jets in proton-proton collisions at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1707}, 121 (2017).
  %doi:10.1007/JHEP07(2017)121
  %[arXiv:1703.03995 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP07(2017)121;%%
  %21 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017huu}
%\bibitem{Sirunyan:2017huu} 
\item CMS Collaboration, ``Measurement of the top quark mass using single top quark events in proton-proton collisions at $\sqrt{s}= 8$  TeV'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 5, 354 (2017).
  %doi:10.1140/epjc/s10052-017-4912-8
  %[arXiv:1703.02530 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-4912-8;%%
  %6 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017hci}
%\bibitem{Sirunyan:2017hci} 
\item CMS Collaboration, ``Search for dark matter produced with an energetic jet or a hadronically decaying W or Z boson at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1707}, 014 (2017).
  %doi:10.1007/JHEP07(2017)014
  %[arXiv:1703.01651 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP07(2017)014;%%
  %51 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017azo}
%\bibitem{Sirunyan:2017azo} 
\item CMS Collaboration, ``Measurement of double-differential cross sections for top quark pair production in pp collisions at $\sqrt{s} = 8$ $\,\text {TeV}$ and impact on parton distribution functions'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 7, 459 (2017).
  %doi:10.1140/epjc/s10052-017-4984-5
  %[arXiv:1703.01630 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-4984-5;%%
  %14 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017tep}
%\bibitem{Sirunyan:2017tep} 
\item CMS Collaboration, ``Search for standard model production of four top quarks in proton-proton collisions at $\sqrt{s}$ = 13 TeV'', Phys.\ Lett.\ B {\bf 772}, 336 (2017).
  %doi:10.1016/j.physletb.2017.06.064
  %[arXiv:1702.06164 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.06.064;%%
  %10 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2017jub}
%\bibitem{Khachatryan:2017jub} 
\item CMS Collaboration, ``Measurement of the cross section for electroweak production of Z$\gamma$ in association with two jets and constraints on anomalous quartic gauge couplings in proton-proton collisions at $\sqrt{s} = 8$ TeV'', Phys.\ Lett.\ B {\bf 770}, 380 (2017).
  %doi:10.1016/j.physletb.2017.04.071
  %[arXiv:1702.03025 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.04.071;%%
  %5 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017mzd}
%\bibitem{Sirunyan:2017mzd} 
\item CMS Collaboration, ``Measurement of prompt and nonprompt $\mathrm{J}/{\psi }$ production in $\mathrm {p}\mathrm {p}$ and $\mathrm {p}\mathrm {Pb}$ collisions at $\sqrt{s_{\mathrm {NN}}} =5.02\,\text {TeV} $'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 4, 269 (2017).
  %doi:10.1140/epjc/s10052-017-4828-3
  %[arXiv:1702.01462 [nucl-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-4828-3;%%
  %8 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017kkr}
%\bibitem{Sirunyan:2017kkr} 
\item CMS Collaboration, ``Search for associated production of a Z boson with a single top quark and for tZ flavour-changing interactions in pp collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1707}, 003 (2017).
  %doi:10.1007/JHEP07(2017)003
  %[arXiv:1702.01404 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP07(2017)003;%%
  %24 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017jic}
%\bibitem{Sirunyan:2017jic} 
\item CMS Collaboration, ``Study of Jet Quenching with $Z+\text{jet}$ Correlations in Pb-Pb and $pp$ Collisions at ${\sqrt{s}}_{NN}=5.02\text{ }\text{ }\mathrm{TeV}$'', Phys.\ Rev.\ Lett.\  {\bf 119}, no. 8, 082301 (2017).
  %doi:10.1103/PhysRevLett.119.082301
  %[arXiv:1702.01060 [nucl-ex]].
  %%CITATION = %doi:10.1103/PhysRevLett.119.082301;%%
  %14 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017pan}
%\bibitem{Sirunyan:2017pan} 
\item CMS Collaboration, ``Azimuthal anisotropy of charged particles with transverse momentum up to 100 GeV/ c in PbPb collisions at $\sqrt {s}_{{NN}}$=5.02 TeV'', Phys.\ Lett.\ B {\bf 776}, 195 (2018).
  %doi:10.1016/j.physletb.2017.11.041
  %[arXiv:1702.00630 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.11.041;%%
  %15 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017nsj}
%\bibitem{Sirunyan:2017nsj} 
\item CMS Collaboration, ``Measurement of the inclusive energy spectrum in the very forward direction in proton-proton collisions at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1708}, 046 (2017).
  %doi:10.1007/JHEP08(2017)046
  %[arXiv:1701.08695 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP08(2017)046;%%
  %3 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017tfc}
%\bibitem{Sirunyan:2017tfc} 
\item CMS Collaboration, ``Search for single production of vector-like quarks decaying into a b quark and a W boson in proton-proton collisions at $\sqrt s =$ 13 TeV'', Phys.\ Lett.\ B {\bf 772}, 634 (2017).
  %doi:10.1016/j.physletb.2017.07.022
  %[arXiv:1701.08328 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.07.022;%%
  %8 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017ezy}
%\bibitem{Sirunyan:2017ezy} 
\item CMS Collaboration, ``Search for single production of vector-like quarks decaying to a Z boson and a top or a bottom quark in proton-proton collisions at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1705}, 029 (2017).
  %doi:10.1007/JHEP05(2017)029
  %[arXiv:1701.07409 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP05(2017)029;%%
  %14 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2017qgo}
%\bibitem{Khachatryan:2017qgo} 
\item CMS Collaboration, ``Search for new phenomena with multiple charged leptons in proton-proton collisions at $\sqrt{s}= 13$ $\,\text {TeV}$'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 9, 635 (2017).
  %doi:10.1140/epjc/s10052-017-5182-1
  %[arXiv:1701.06940 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-5182-1;%%
  %9 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017uhy}
%\bibitem{Sirunyan:2017uhy} 
\item CMS Collaboration, ``Measurement of the $t \bar t$ production cross section using events with one lepton and at least one jet in pp collisions at $\sqrt{s}$  = 13 TeV'', JHEP {\bf 1709}, 051 (2017).
  %doi:10.1007/JHEP09(2017)051
  %[arXiv:1701.06228 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP09(2017)051;%%
  %18 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017onm}
%\bibitem{Sirunyan:2017onm} 
\item CMS Collaboration, ``Search for dark matter and unparticles in events with a Z boson and missing transverse momentum in proton-proton collisions at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1703}, 061 (2017).
  Erratum: [JHEP {\bf 1709}, 106 (2017).]
  %doi:10.1007/JHEP09(2017)106, 10.1007/JHEP03(2017)061
  %[arXiv:1701.02042 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP09(2017)106, 10.1007/JHEP03(2017)061;%%
  %20 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2017mnf}
%\bibitem{Khachatryan:2017mnf} 
\item CMS Collaboration, ``Search for light bosons in decays of the 125 GeV Higgs boson in proton-proton collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1710}, 076 (2017).
  %doi:10.1007/JHEP10(2017)076
  %[arXiv:1701.02032 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP10(2017)076;%%
  %20 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017rbc}
%\bibitem{Sirunyan:2017rbc} 
\item CMS Collaboration, ``Mechanical stability of the CMS strip tracker measured with a laser alignment system'', JINST {\bf 12}, no. 04, P04023 (2017).
  %doi:10.1088/1748-0221/12/04/P04023
  %[arXiv:1701.02022 [physics.ins-det]].
  %%CITATION = %doi:10.1088/1748-0221/12/04/P04023;%%

%\cite{Khachatryan:2017rhw}
%\bibitem{Khachatryan:2017rhw} 
\item CMS Collaboration, ``Search for supersymmetry in the all-hadronic final state using top quark tagging in pp collisions at $\sqrt s = 13$ TeV'', Phys.\ Rev.\ D {\bf 96}, no. 1, 012004 (2017).
  %doi:10.1103/PhysRevD.96.012004
  %[arXiv:1701.01954 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevD.96.012004;%%
  %15 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2017wny}
%\bibitem{Khachatryan:2017wny} 
\item CMS Collaboration, ``Search for leptophobic Z' bosons decaying into four-lepton final states in proton-proton collisions at $\sqrt s$ =8TeV'', Phys.\ Lett.\ B {\bf 773}, 563 (2017).
  %doi:10.1016/j.physletb.2017.08.069
  %[arXiv:1701.01345 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.08.069;%%
  %4 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2016wqt}
%\bibitem{Sirunyan:2016wqt} 
\item CMS Collaboration, ``Search for high-mass $\mathrm{ Z }\gamma$ resonances in proton-proton collisions at $\sqrt{s}=$ 8 and 13 TeV using jet substructure techniques'', Phys.\ Lett.\ B {\bf 772}, 363 (2017).
  %doi:10.1016/j.physletb.2017.06.062
  %[arXiv:1612.09516 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.06.062;%%
  %7 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016jww}
%\bibitem{Khachatryan:2016jww} 
\item CMS Collaboration, ``Search for heavy gauge W' boson in events with an energetic lepton and large missing transverse momentum at $ \sqrt{s} = $ 13 TeV'', Phys.\ Lett.\ B {\bf 770}, 278 (2017).
  %doi:10.1016/j.physletb.2017.04.043
  %[arXiv:1612.09274 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.04.043;%%
  %18 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016vif}
%\bibitem{Khachatryan:2016vif} 
\item CMS Collaboration, ``Measurement of electroweak-induced production of W$\gamma$ with two jets in pp collisions at $ \sqrt{s}=8 $ TeV and constraints on anomalous quartic gauge couplings'', JHEP {\bf 1706}, 106 (2017).
  %doi:10.1007/JHEP06(2017)106
  %[arXiv:1612.09256 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP06(2017)106;%%
  %4 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2016cao}
%\bibitem{Sirunyan:2016cao} 
\item CMS Collaboration, ``Search for massive resonances decaying into WW, WZ or ZZ bosons in proton-proton collisions at $\sqrt{s} = $ 13 TeV'', JHEP {\bf 1703}, 162 (2017).
  %doi:10.1007/JHEP03(2017)162
  %[arXiv:1612.09159 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP03(2017)162;%%
  %21 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2016fcs}
%\bibitem{Sirunyan:2016fcs} 
\item CMS Collaboration, ``Measurements of the charm jet cross section and nuclear modification factor in pPb collisions at $\sqrt{{s}_{NN}}$ = 5.02 TeV'', Phys.\ Lett.\ B {\bf 772}, 306 (2017).
  %doi:10.1016/j.physletb.2017.06.053
  %[arXiv:1612.08972 [nucl-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.06.053;%%
  %5 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2016ipo}
%\bibitem{Sirunyan:2016ipo} 
\item CMS Collaboration, ``Search for electroweak production of a vector-like quark decaying to a top quark and a Higgs boson using boosted topologies in fully hadronic final states'', JHEP {\bf 1704}, 136 (2017).
  %doi:10.1007/JHEP04(2017)136
  %[arXiv:1612.05336 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP04(2017)136;%%
  %9 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2016jpr}
%\bibitem{Sirunyan:2016jpr} 
\item CMS Collaboration, ``Searches for pair production of third-generation squarks in $\sqrt{s}=13$ $\,\text {TeV}$ pp collisions'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 5, 327 (2017).
  %doi:10.1140/epjc/s10052-017-4853-2
  %[arXiv:1612.03877 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-4853-2;%%
  %25 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016jqo}
%\bibitem{Khachatryan:2016jqo} 
\item CMS Collaboration, ``Search for heavy neutrinos or third-generation leptoquarks in final states with two hadronically decaying $\tau$ leptons and two jets in proton-proton collisions at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1703}, 077 (2017).
  %doi:10.1007/JHEP03(2017)077
  %[arXiv:1612.01190 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP03(2017)077;%%
  %20 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016vph}
%\bibitem{Khachatryan:2016vph} 
\item CMS Collaboration, ``Search for single production of a heavy vector-like T quark decaying to a Higgs boson and a top quark with a lepton and jets in the final state'', Phys.\ Lett.\ B {\bf 771}, 80 (2017).
  %doi:10.1016/j.physletb.2017.05.019
  %[arXiv:1612.00999 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.05.019;%%
  %14 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016ngh}
%\bibitem{Khachatryan:2016ngh} 
\item CMS Collaboration, ``Search for CP violation in $ t\overline{t} $ production and decay in proton-proton collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1703}, 101 (2017).
  %doi:10.1007/JHEP03(2017)101
  %[arXiv:1611.08931 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP03(2017)101;%%
  %8 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016ojf}
%\bibitem{Khachatryan:2016ojf} 
\item CMS Collaboration, ``Search for supersymmetry in events with photons and missing transverse energy in pp collisions at 13 TeV'', Phys.\ Lett.\ B {\bf 769}, 391 (2017).
  %doi:10.1016/j.physletb.2017.04.005
  %[arXiv:1611.06604 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.04.005;%%
  %7 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016qkc}
%\bibitem{Khachatryan:2016qkc} 
\item CMS Collaboration, ``Search for heavy resonances decaying to tau lepton pairs in proton-proton collisions at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1702}, 048 (2017).
  %doi:10.1007/JHEP02(2017)048
  %[arXiv:1611.06594 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP02(2017)048;%%
  %11 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016iob}
%\bibitem{Khachatryan:2016iob} 
\item CMS Collaboration, ``Measurements of the associated production of a Z boson and b jets in pp collisions at ${\sqrt{s}} = 8\,\text {TeV} $'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 11, 751 (2017).
  %doi:10.1140/epjc/s10052-017-5140-y
  %[arXiv:1611.06507 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-5140-y;%%
  %7 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016kzg}
%\bibitem{Khachatryan:2016kzg} 
\item CMS Collaboration, ``Measurement of the $t\bar{t}$ production cross section using events in the e$\mu$ final state in pp collisions at $\sqrt{s} =$ 13 TeV'', Eur.\ Phys.\ J.\ C {\bf 77}, 172 (2017).
  %doi:10.1140/epjc/s10052-017-4718-8
  %[arXiv:1611.04040 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-4718-8;%%
  %26 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016crw}
%\bibitem{Khachatryan:2016crw} 
\item CMS Collaboration, ``Measurements of differential production cross sections for a Z boson in association with jets in pp collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1704}, 022 (2017).
  %doi:10.1007/JHEP04(2017)022
  %[arXiv:1611.03844 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP04(2017)022;%%
  %10 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2016iap}
%\bibitem{Sirunyan:2016iap} 
\item CMS Collaboration, ``Search for dijet resonances in proton-proton collisions at $\sqrt{s}$ = 13 TeV and constraints on dark matter and other models'', Phys.\ Lett.\ B {\bf 769}, 520 (2017).
  Erratum: [Phys.\ Lett.\ B {\bf 772}, 882 (2017).]
  %doi:10.1016/j.physletb.2017.09.029, 10.1016/j.physletb.2017.02.012
  %[arXiv:1611.03568 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.09.029, 10.1016/j.physletb.2017.02.012;%%
  %65 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016odn}
%\bibitem{Khachatryan:2016odn} 
\item CMS Collaboration, ``Charged-particle nuclear modification factors in PbPb and pPb collisions at $ \sqrt{s_{\mathrm{N}\;\mathrm{N}}}=5.02 $ TeV'', JHEP {\bf 1704}, 039 (2017).
  %doi:10.1007/JHEP04(2017)039
  %[arXiv:1611.01664 [nucl-ex]].
  %%CITATION = %doi:10.1007/JHEP04(2017)039;%%
  %47 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016xxp}
%\bibitem{Khachatryan:2016xxp} 
\item CMS Collaboration, ``Suppression of $\Upsilon(1S), \Upsilon(2S)$ and $\Upsilon(3S)$ production in PbPb collisions at $\sqrt{s_{\rm NN}}$ = 2.76 TeV'', Phys.\ Lett.\ B {\bf 770}, 357 (2017).
  %doi:10.1016/j.physletb.2017.04.031
  %[arXiv:1611.01510 [nucl-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.04.031;%%
  %26 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2016znt}
%\bibitem{Sirunyan:2016znt} 
\item CMS Collaboration, ``Relative Modification of Prompt $\psi$ (2S) and J/$\psi$ Yields from pp to PbPb Collisions at $\sqrt{s_{NN}}=5.02$ TeV'', Phys.\ Rev.\ Lett.\  {\bf 118}, no. 16, 162301 (2017).
  %doi:10.1103/PhysRevLett.118.162301
  %[arXiv:1611.01438 [nucl-ex]].
  %%CITATION = %doi:10.1103/PhysRevLett.118.162301;%%
  %18 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016dvc}
%\bibitem{Khachatryan:2016dvc} 
\item CMS Collaboration, ``A search for new phenomena in pp collisions at $\sqrt{s} = 13\,\text {TeV} $ in final states with missing transverse momentum and at least one jet using the $\alpha _{\mathrm {T}}$ variable'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 5, 294 (2017).
  %doi:10.1140/epjc/s10052-017-4787-8
  %[arXiv:1611.00338 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-4787-8;%%
  %22 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016whc}
%\bibitem{Khachatryan:2016whc} 
\item CMS Collaboration, ``Searches for invisible decays of the Higgs boson in pp collisions at $\sqrt{s}$ = 7, 8, and 13 TeV'', JHEP {\bf 1702}, 135 (2017).
  %doi:10.1007/JHEP02(2017)135
  %[arXiv:1610.09218 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP02(2017)135;%%
  %65 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016cfx}
%\bibitem{Khachatryan:2016cfx} 
\item CMS Collaboration, ``Search for heavy resonances decaying into a vector boson and a Higgs boson in final states with charged leptons, neutrinos, and b quarks'', Phys.\ Lett.\ B {\bf 768}, 137 (2017).
  %doi:10.1016/j.physletb.2017.02.040
  %[arXiv:1610.08066 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.02.040;%%
  %18 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016ydm}
%\bibitem{Khachatryan:2016ydm} 
\item CMS Collaboration, ``Observation of $\Upsilon$(1S) pair production in proton-proton collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1705}, 013 (2017).
  %doi:10.1007/JHEP05(2017)013
  %[arXiv:1610.07095 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP05(2017)013;%%
  %17 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016unx}
%\bibitem{Khachatryan:2016unx} 
\item CMS Collaboration, ``Search for R-parity violating supersymmetry with displaced vertices in proton-proton collisions at $\sqrt{s}$ = 8 TeV'', Phys.\ Rev.\ D {\bf 95}, no. 1, 012009 (2017).
  %doi:10.1103/PhysRevD.95.012009
  %[arXiv:1610.05133 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevD.95.012009;%%
  %6 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016trj}
%\bibitem{Khachatryan:2016trj} 
\item CMS Collaboration, ``Search for electroweak production of charginos in final states with two $\tau$ leptons in pp collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1704}, 018 (2017).
  %doi:10.1007/JHEP04(2017)018
  %[arXiv:1610.04870 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP04(2017)018;%%
  %7 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016atv}
%\bibitem{Khachatryan:2016atv} 
\item CMS Collaboration, ``Search for top quark decays via Higgs-boson-mediated flavor-changing neutral currents in pp collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1702}, 079 (2017).
  %doi:10.1007/JHEP02(2017)079
  %[arXiv:1610.04857 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP02(2017)079;%%
  %24 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016fue}
%\bibitem{Khachatryan:2016fue} 
\item CMS Collaboration, ``Measurements of differential cross sections for associated production of a W boson and jets in proton-proton collisions at $\sqrt{s} =$ 8 TeV'', Phys.\ Rev.\ D {\bf 95}, 052002 (2017).
  %doi:10.1103/PhysRevD.95.052002
  %[arXiv:1610.04222 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevD.95.052002;%%
  %10 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016mnb}
%\bibitem{Khachatryan:2016mnb} 
\item CMS Collaboration, ``Measurement of differential cross sections for top quark pair production using the lepton+jets final state in proton-proton collisions at 13 TeV'', Phys.\ Rev.\ D {\bf 95}, no. 9, 092001 (2017).
  %doi:10.1103/PhysRevD.95.092001
  %[arXiv:1610.04191 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevD.95.092001;%%
  %38 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016sib}
%\bibitem{Khachatryan:2016sib} 
\item CMS Collaboration, ``Search for anomalous Wtb couplings and flavour-changing neutral currents in t-channel single top quark production in pp collisions at $\sqrt{s} =$ 7 and 8 TeV'', JHEP {\bf 1702}, 028 (2017).
  %doi:10.1007/JHEP02(2017)028
  %[arXiv:1610.03545 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP02(2017)028;%%
  %21 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016odk}
%\bibitem{Khachatryan:2016odk} 
\item CMS Collaboration, ``Search for high-mass Z$\gamma$ resonances in $\mathrm{ e }^{+}\mathrm{ e }^{-}\gamma $ and $ \mu^{+}\mu^{-}\gamma$ final states in proton-proton collisions at $\sqrt{s} =$ 8 and 13 TeV'', JHEP {\bf 1701}, 076 (2017).
  %doi:10.1007/JHEP01(2017)076
  %[arXiv:1610.02960 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP01(2017)076;%%
  %9 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2016cdg}
%\bibitem{Sirunyan:2016cdg} 
\item CMS Collaboration, ``Cross section measurement of $t$-channel single top quark production in pp collisions at $\sqrt s =$ 13 TeV'', Phys.\ Lett.\ B {\bf 772}, 752 (2017).
  %doi:10.1016/j.physletb.2017.07.047
  %[arXiv:1610.00678 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.07.047;%%
  %38 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016ypw}
%\bibitem{Khachatryan:2016ypw} 
\item CMS Collaboration, ``Suppression and azimuthal anisotropy of prompt and nonprompt ${\mathrm{J}}/\psi $ production in PbPb collisions at $\sqrt{{s_{_{\text {NN}}}}} =2.76$ $\,\mathrm{TeV}$'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 4, 252 (2017).
  %doi:10.1140/epjc/s10052-017-4781-1
  %[arXiv:1610.00613 [nucl-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-4781-1;%%
  %23 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016got}
%\bibitem{Khachatryan:2016got} 
\item CMS Collaboration, ``Observation of charge-dependent azimuthal correlations in $p$-Pb collisions and its implication for the search for the chiral magnetic effect'', Phys.\ Rev.\ Lett.\  {\bf 118}, no. 12, 122301 (2017).
  %doi:10.1103/PhysRevLett.118.122301
  %[arXiv:1610.00263 [nucl-ex]].
  %%CITATION = %doi:10.1103/PhysRevLett.118.122301;%%
  %43 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016xdt}
%\bibitem{Khachatryan:2016xdt} 
\item CMS Collaboration, ``Search for supersymmetry in events with one lepton and multiple jets in proton-proton collisions at $\sqrt{s} =$ 13 TeV'', Phys.\ Rev.\ D {\bf 95}, no. 1, 012011 (2017).
  %doi:10.1103/PhysRevD.95.012011
  %[arXiv:1609.09386 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevD.95.012011;%%
  %13 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016sfv}
%\bibitem{Khachatryan:2016sfv} 
\item CMS Collaboration, ``Search for long-lived charged particles in proton-proton collisions at $\sqrt{s}=$ 13 TeV'', Phys.\ Rev.\ D {\bf 94}, no. 11, 112004 (2016).
  %doi:10.1103/PhysRevD.94.112004
  %[arXiv:1609.08382 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevD.94.112004;%%
  %34 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016epu}
%\bibitem{Khachatryan:2016epu} 
\item CMS Collaboration, ``Inclusive search for supersymmetry using razor variables in pp collisions at $\sqrt{s}=$ 13 TeV'', Phys.\ Rev.\ D {\bf 95}, no. 1, 012003 (2017).
  %doi:10.1103/PhysRevD.95.012003
  %[arXiv:1609.07658 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevD.95.012003;%%
  %24 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016poo}
%\bibitem{Khachatryan:2016poo} 
\item CMS Collaboration, ``Measurement of the WZ production cross section in pp collisions at $\sqrt{s} = 7$ and 8 $\,\text{TeV}$ and search for anomalous triple gauge couplings at $\sqrt{s} = 8\,\text{TeV} $'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 4, 236 (2017).
  %doi:10.1140/epjc/s10052-017-4730-z
  %[arXiv:1609.05721 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-4730-z;%%
  %12 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016zqb}
%\bibitem{Khachatryan:2016zqb} 
\item CMS Collaboration, ``Search for narrow resonances in dilepton mass spectra in proton-proton collisions at $\sqrt{s}$ = 13 TeV and combination with 8 TeV data'', Phys.\ Lett.\ B {\bf 768}, 57 (2017).
  %doi:10.1016/j.physletb.2017.02.010
  %[arXiv:1609.05391 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.02.010;%%
  %52 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016jfl}
%\bibitem{Khachatryan:2016jfl} 
\item CMS Collaboration, ``Measurement of inclusive jet cross sections in $pp$ and PbPb collisions at $\sqrt{s_{NN}}=$ 2.76 TeV'', Phys.\ Rev.\ C {\bf 96}, no. 1, 015202 (2017).
  %doi:10.1103/PhysRevC.96.015202
  %[arXiv:1609.05383 [nucl-ex]].
  %%CITATION = %doi:10.1103/PhysRevC.96.015202;%%
  %29 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016mlc}
%\bibitem{Khachatryan:2016mlc} 
\item CMS Collaboration, ``Measurement and QCD analysis of double-differential inclusive jet cross sections in pp collisions at $ \sqrt{s}=8 $ TeV and cross section ratios to 2.76 and 7 TeV'', JHEP {\bf 1703}, 156 (2017).
  %doi:10.1007/JHEP03(2017)156
  %[arXiv:1609.05331 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP03(2017)156;%%
  %31 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016rjt}
%\bibitem{Khachatryan:2016rjt} 
\item CMS Collaboration, ``Studies of inclusive four-jet production with two $b$-tagged jets in proton-proton collisions at 7 TeV'', Phys.\ Rev.\ D {\bf 94}, no. 11, 112005 (2016).
  %doi:10.1103/PhysRevD.94.112005
  %[arXiv:1609.03489 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevD.94.112005;%%
  %2 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016yec}
%\bibitem{Khachatryan:2016yec} 
\item CMS Collaboration, ``Search for high-mass diphoton resonances in proton-proton collisions at 13 TeV and combination with 8 TeV search'', Phys.\ Lett.\ B {\bf 767}, 147 (2017).
  %doi:10.1016/j.physletb.2017.01.027
  %[arXiv:1609.02507 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.01.027;%%
  %61 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016tfj}
%\bibitem{Khachatryan:2016tfj} 
\item CMS Collaboration, ``Decomposing transverse momentum balance contributions for quenched jets in PbPb collisions at $ \sqrt{s_{\mathrm{N}\;\mathrm{N}}}=2.76 $ TeV'', JHEP {\bf 1611}, 055 (2016).
  %doi:10.1007/JHEP11(2016)055
  %[arXiv:1609.02466 [nucl-ex]].
  %%CITATION = %doi:10.1007/JHEP11(2016)055;%%
  %14 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016bia}
%\bibitem{Khachatryan:2016bia} 
\item CMS Collaboration, ``The CMS trigger system'', JINST {\bf 12}, no. 01, P01020 (2017).
  %doi:10.1088/1748-0221/12/01/P01020
  %[arXiv:1609.02366 [physics.ins-det]].
  %%CITATION = %doi:10.1088/1748-0221/12/01/P01020;%%
  %100 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016csy}
%\bibitem{Khachatryan:2016csy} 
\item CMS Collaboration, ``Measurement of the total and differential inclusive $B^+$ hadron cross sections in pp collisions at $\sqrt{s}$ = 13 TeV'', Phys.\ Lett.\ B {\bf 771}, 435 (2017).
  %doi:10.1016/j.physletb.2017.05.074
  %[arXiv:1609.00873 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.05.074;%%
  %13 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016ipq}
%\bibitem{Khachatryan:2016ipq} 
\item CMS Collaboration, ``Measurement of the production cross section of a W boson in association with two b jets in pp collisions at $\sqrt{s} = 8{\,\mathrm{{TeV}}} $'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 2, 92 (2017).
  %doi:10.1140/epjc/s10052-016-4573-z
  %[arXiv:1608.07561 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-016-4573-z;%%
  %10 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016pek}
%\bibitem{Khachatryan:2016pek} 
\item CMS Collaboration, ``Measurement of the mass of the top quark in decays with a $J/\psi$ meson in pp collisions at 8 TeV'', JHEP {\bf 1612}, 123 (2016).
  %doi:10.1007/JHEP12(2016)123
  %[arXiv:1608.03560 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP12(2016)123;%%
  %6 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016xim}
%\bibitem{Khachatryan:2016xim} 
\item CMS Collaboration, ``Search for new phenomena in events with high jet multiplicity and low missing transverse momentum in proton-proton collisions at $\sqrt{s}=8$ TeV'', Phys.\ Lett.\ B {\bf 770}, 257 (2017).
  %doi:10.1016/j.physletb.2017.01.073
  %[arXiv:1608.01224 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.01.073;%%
  %5 citations counted in INSPIRE as of 12 Jan 2018
  
%\cite{Khachatryan:2016txa}
%\bibitem{Khachatryan:2016txa}
\item CMS Collaboration, ``Measurement of the ZZ production cross section and Z $\to \ell^+\ell^-\ell'^+\ell'^-$ branching fraction in pp collisions at $\sqrt s$=13 TeV'', Phys.\ Lett.\ B {\bf 763}, 280 (2016), Erratum: [Phys.\ Lett.\ B {\bf 772}, 884 (2017)].
%  doi:10.1016/j.physletb.2017.09.030, 10.1016/j.physletb.2016.10.054
%  [arXiv:1607.08834 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2017.09.030, 10.1016/j.physletb.2016.10.054;%%
  %28 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016qkk}
%\bibitem{Khachatryan:2016qkk}
\item CMS Collaboration, ``Measurement of electroweak production of a W boson and two forward jets in proton-proton collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1611}, 147 (2016).
%  doi:10.1007/JHEP11(2016)147
%  [arXiv:1607.06975 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP11(2016)147;%%
  %6 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016tgp}
%\bibitem{Khachatryan:2016tgp}
\item CMS Collaboration, ``Measurement of the WZ production cross section in pp collisions at $\sqrt(s) =$ 13 TeV'', Phys.\ Lett.\ B {\bf 766}, 268 (2017)
%  doi:10.1016/j.physletb.2017.01.011
%  [arXiv:1607.06943 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2017.01.011;%%
  %34 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016mdm}
%\bibitem{Khachatryan:2016mdm}
\item CMS Collaboration, ``Search for dark matter in proton-proton collisions at 8 TeV with missing transverse momentum and vector boson tagged jets'', JHEP {\bf 1612}, 083 (2016), Erratum: [JHEP {\bf 1708}, 035 (2017)].
%  doi:10.1007/JHEP12(2016)083, 10.1007/JHEP08(2017)035
%  [arXiv:1607.05764 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP12(2016)083, 10.1007/JHEP08(2017)035;%%
  %25 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016kdb}
%\bibitem{Khachatryan:2016kdb}
\item CMS Collaboration, ``Jet energy scale and resolution in the CMS experiment in pp collisions at 8 TeV'', JINST {\bf 12}, no. 02, P02014 (2017)
%  doi:10.1088/1748-0221/12/02/P02014
%  [arXiv:1607.03663 [hep-ex]].
  %%CITATION = doi:10.1088/1748-0221/12/02/P02014;%%
  %159 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016rke}
%\bibitem{Khachatryan:2016rke}
\item CMS Collaboration, ``Search for lepton flavour violating decays of the Higgs boson to $e \tau$ and $e \mu$ in proton–proton collisions at $\sqrt s=$ 8 TeV'', Phys.\ Lett.\ B {\bf 763}, 472 (2016).
%  doi:10.1016/j.physletb.2016.09.062
%  [arXiv:1607.03561 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.09.062;%%
  %21 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016npv}
%\bibitem{Khachatryan:2016npv}
\item CMS Collaboration, ``Observation of the decay $B^+ \to \psi(2S) \phi(1020) K^+$ in pp collisions at $\sqrt s =$ 8 TeV'', Phys.\ Lett.\ B {\bf 764}, 66 (2017)
%  doi:10.1016/j.physletb.2016.11.001
%  [arXiv:1607.02638 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.11.001;%%
  %1 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016fll}
%\bibitem{Khachatryan:2016fll}
\item CMS Collaboration, ``Search for new physics in final states with two opposite-sign, same-flavor leptons, jets, and missing transverse momentum in pp collisions at sqrt(s) = 13 TeV'', JHEP {\bf 1612}, 013 (2016).
%  doi:10.1007/JHEP12(2016)013
%  [arXiv:1607.00915 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP12(2016)013;%%
  %21 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016oou}
%\bibitem{Khachatryan:2016oou}
\item CMS Collaboration, ``Measurement of the differential cross sections for top quark pair production as a function of kinematic event variables in pp collisions at $\sqrt s$=7 and 8 TeV'', Phys.\ Rev.\ D {\bf 94}, no. 5, 052006 (2016).
%  doi:10.1103/PhysRevD.94.052006
%  [arXiv:1607.00837 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.94.052006;%%
  %7 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016iqn}
%\bibitem{Khachatryan:2016iqn}
\item CMS Collaboration, ``Searches for $R$-parity-violating supersymmetry in $pp $collisions at $\sqrt(s) =$ 8 TeV in final states with 0-4 leptons'', Phys.\ Rev.\ D {\bf 94}, no. 11, 112009 (2016).
%  doi:10.1103/PhysRevD.94.112009
%  [arXiv:1606.08076 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.94.112009;%%
  %12 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016txc}
%\bibitem{Khachatryan:2016txc}
\item CMS Collaboration, ``Evidence for collectivity in pp collisions at the LHC'', Phys.\ Lett.\ B {\bf 765}, 193 (2017)
%  doi:10.1016/j.physletb.2016.12.009
%  [arXiv:1606.06198 [nucl-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.12.009;%%
  %102 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016nbe}
%\bibitem{Khachatryan:2016nbe}
\item CMS Collaboration, ``Measurement of the transverse momentum spectra of weak vector bosons produced in proton-proton collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1702}, 096 (2017)
%  doi:10.1007/JHEP02(2017)096
%  [arXiv:1606.05864 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP02(2017)096;%%
  %14 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016hje}
%\bibitem{Khachatryan:2016hje}
\item CMS Collaboration, ``Search for Resonant Production of High-Mass Photon Pairs in Proton-Proton Collisions at $\sqrt s$ =8 and 13 TeV'', Phys.\ Rev.\ Lett.\  {\bf 117}, no. 5, 051802 (2016).
%  doi:10.1103/PhysRevLett.117.051802
%  [arXiv:1606.04093 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevLett.117.051802;%%
  %119 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016nvf}
%\bibitem{Khachatryan:2016nvf}
\item CMS Collaboration, ``Phenomenological MSSM interpretation of CMS searches in pp collisions at sqrt(s) = 7 and 8 TeV'', JHEP {\bf 1610}, 129 (2016).
%  doi:10.1007/JHEP10(2016)129
%  [arXiv:1606.03577 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP10(2016)129;%%
  %22 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016vnn}
%\bibitem{Khachatryan:2016vnn}
\item CMS Collaboration, ``Measurement of the transverse momentum spectrum of the Higgs boson produced in pp collisions at $ \sqrt{s}=8 $ TeV using $H \to WW$ decays'', JHEP {\bf 1703}, 032 (2017)
%  doi:10.1007/JHEP03(2017)032
%  [arXiv:1606.01522 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP03(2017)032;%%
  %18 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016mbu}
%\bibitem{Khachatryan:2016mbu}
\item CMS Collaboration, ``Search for Dark Matter and Supersymmetry with a Compressed Mass Spectrum in the Vector Boson Fusion Topology in Proton-Proton Collisions at $\sqrt{s} =$ 8 TeV'', Phys.\ Rev.\ Lett.\  {\bf 118}, no. 2, 021802 (2017)
%  doi:10.1103/PhysRevLett.118.021802
%  [arXiv:1605.09305 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevLett.118.021802;%%
  %10 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016fky}
%\bibitem{Khachatryan:2016fky}
\item CMS Collaboration, ``Measurement of the W boson helicity fractions in the decays of top quark pairs to lepton $+$ jets final states produced in pp collisions at $\sqrt s=$ 8TeV'', Phys.\ Lett.\ B {\bf 762}, 512 (2016).
%  doi:10.1016/j.physletb.2016.10.007
%  [arXiv:1605.09047 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.10.007;%%
  %20 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016pxa}
%\bibitem{Khachatryan:2016pxa}
\item CMS Collaboration, ``Search for top squark pair production in compressed-mass-spectrum scenarios in proton-proton collisions at $\sqrt{s}$ = 8 TeV using the $\alpha_T$ variable'', Phys.\ Lett.\ B {\bf 767}, 403 (2017)
%  doi:10.1016/j.physletb.2017.02.007
%  [arXiv:1605.08993 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2017.02.007;%%
  %21 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016qhq}
%\bibitem{Khachatryan:2016qhq}
\item CMS Collaboration, ``Coherent $J/\psi$ photoproduction in ultra-peripheral PbPb collisions at $\sqrt {s_{NN}} =$ 2.76 TeV with the CMS experiment'', Phys.\ Lett.\ B {\bf 772}, 489 (2017)
%  doi:10.1016/j.physletb.2017.07.001
%  [arXiv:1605.06966 [nucl-ex]].
  %%CITATION = doi:10.1016/j.physletb.2017.07.001;%%
  %21 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016yru}
%\bibitem{Khachatryan:2016yru}
\item CMS Collaboration, ``Multiplicity and rapidity dependence of strange hadron production in pp, pPb, and PbPb collisions at the LHC'', Phys.\ Lett.\ B {\bf 768}, 103 (2017)
%  doi:10.1016/j.physletb.2017.01.075
%  [arXiv:1605.06699 [nucl-ex]].
  %%CITATION = doi:10.1016/j.physletb.2017.01.075;%%
  %20 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016uwr}
%\bibitem{Khachatryan:2016uwr}
\item CMS Collaboration, ``Search for supersymmetry in pp collisions at $ \sqrt{s}=13 $ TeV in the single-lepton final state using the sum of masses of large-radius jets'', JHEP {\bf 1608}, 122 (2016).
%  doi:10.1007/JHEP08(2016)122
%  [arXiv:1605.04608 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP08(2016)122;%%
  %34 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016wdh}
%\bibitem{Khachatryan:2016wdh}
\item CMS Collaboration, ``Measurement of the double-differential inclusive jet cross section in proton–proton collisions at $\sqrt{s} = 13\,\text {TeV} $'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 8, 451 (2016).
%  doi:10.1140/epjc/s10052-016-4286-3
%  [arXiv:1605.04436 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4286-3;%%
  %30 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016kod}
%\bibitem{Khachatryan:2016kod}
\item CMS Collaboration, ``Search for new physics in same-sign dilepton events in proton–proton collisions at $\sqrt{s} = 13\,\text {TeV} $'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 8, 439 (2016).
%  doi:10.1140/epjc/s10052-016-4261-z
%  [arXiv:1605.03171 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4261-z;%%
  %47 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016ctc}
%\bibitem{Khachatryan:2016ctc}
\item CMS Collaboration, ``Search for Higgs boson off-shell production in proton-proton collisions at 7 and 8 TeV and derivation of constraints on its total decay width'', JHEP {\bf 1609}, 051 (2016).
%  doi:10.1007/JHEP09(2016)051
%  [arXiv:1605.02329 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP09(2016)051;%%
  %21 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016gxp}
%\bibitem{Khachatryan:2016gxp}
\item CMS Collaboration, ``Measurement of the integrated and differential $t \bar t$ production cross sections for high-$p_t$ top quarks in $pp$ collisions at $\sqrt s =$ 8 TeV'', Phys.\ Rev.\ D {\bf 94}, no. 7, 072002 (2016).
%  doi:10.1103/PhysRevD.94.072002
%  [arXiv:1605.00116 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.94.072002;%%
  %34 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016ecr}
%\bibitem{Khachatryan:2016ecr}
\item CMS Collaboration, ``Search for narrow resonances in dijet final states at $\sqrt(s)=$ 8 TeV with the novel CMS technique of data scouting'', Phys.\ Rev.\ Lett.\  {\bf 117}, no. 3, 031802 (2016).
%  doi:10.1103/PhysRevLett.117.031802
%  [arXiv:1604.08907 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevLett.117.031802;%%
  %63 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016ibd}
%\bibitem{Khachatryan:2016ibd}
\item CMS Collaboration, ``Pseudorapidity dependence of long-range two-particle correlations in $p$Pb collisions at $\sqrt {s_{NN}}=$ 5.02 TeV'', Phys.\ Rev.\ C {\bf 96}, no. 1, 014915 (2017)
%  doi:10.1103/PhysRevC.96.014915
%  [arXiv:1604.05347 [nucl-ex]].
  %%CITATION = doi:10.1103/PhysRevC.96.014915;%%
  %9 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016ovq}
%\bibitem{Khachatryan:2016ovq}
\item CMS Collaboration, ``Search for lepton flavour violating decays of heavy resonances and quantum black holes to an e$\mu$ pair in proton-proton collisions at $\sqrt{s}$ = 8 TeV'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 6, 317 (2016).
%  doi:10.1140/epjc/s10052-016-4149-y
%  [arXiv:1604.05239 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4149-y;%%
  %13 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016mud}
%\bibitem{Khachatryan:2016mud}
\item CMS Collaboration, ``Evidence for exclusive $\gamma\gamma \to W^+ W^-$ production and constraints on anomalous quartic gauge couplings in $pp$ collisions at $ \sqrt{s}=7 $ and 8 TeV'', JHEP {\bf 1608}, 119 (2016).
%  doi:10.1007/JHEP08(2016)119
%  [arXiv:1604.04464 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP08(2016)119;%%
  %33 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016reg}
%\bibitem{Khachatryan:2016reg}
\item CMS Collaboration, ``Search for dark matter particles in proton-proton collisions at $ \sqrt{s}=8 $ TeV using the razor variables'', JHEP {\bf 1612}, 088 (2016).
%  doi:10.1007/JHEP12(2016)088
%  [arXiv:1603.08914 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP12(2016)088;%%
  %11 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016sey}
%\bibitem{Khachatryan:2016sey}
\item CMS Collaboration, ``Search for two Higgs bosons in final states containing two photons and two bottom quarks in proton-proton collisions at 8 TeV'', Phys.\ Rev.\ D {\bf 94}, no. 5, 052012 (2016).
%  doi:10.1103/PhysRevD.94.052012
%  [arXiv:1603.06896 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.94.052012;%%
  %56 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016wqo}
%\bibitem{Khachatryan:2016wqo}
\item CMS Collaboration, ``Measurement of the top quark mass using charged particles in pp collisions at $\sqrt s =$ 8 TeV'', Phys.\ Rev.\ D {\bf 93}, no. 9, 092006 (2016).
%  doi:10.1103/PhysRevD.93.092006
%  [arXiv:1603.06536 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.93.092006;%%
  %23 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016ysn}
%\bibitem{Khachatryan:2016ysn}
\item CMS Collaboration, ``Measurements of $t \bar t$ charge asymmetry using dilepton final states in pp collisions at $\sqrt s=8$ TeV'', Phys.\ Lett.\ B {\bf 760}, 365 (2016).
%  doi:10.1016/j.physletb.2016.07.006
%  [arXiv:1603.06221 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.07.006;%%
  %14 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016xvy}
%\bibitem{Khachatryan:2016xvy}
\item CMS Collaboration, ``Search for new physics with the M$_{T2}$ variable in all-jets final states produced in pp collisions at $ \sqrt{s}=13 $ TeV'', JHEP {\bf 1610}, 006 (2016).
%  doi:10.1007/JHEP10(2016)006
%  [arXiv:1603.04053 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP10(2016)006;%%
  %62 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016are}
%\bibitem{Khachatryan:2016are}
\item CMS Collaboration, ``Search for neutral resonances decaying into a Z boson and a pair of b jets or $\tau$ leptons'', Phys.\ Lett.\ B {\bf 759}, 369 (2016).
%  doi:10.1016/j.physletb.2016.05.087
%  [arXiv:1603.02991 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.05.087;%%
  %22 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016vxr}
%\bibitem{Khachatryan:2016vxr}
\item CMS Collaboration, ``$\Upsilon(\mathrm{nS})$ polarizations versus particle multiplicity in pp collisions at $\sqrt{s} =$ 7 TeV'', Phys.\ Lett.\ B {\bf 761}, 31 (2016).
%  doi:10.1016/j.physletb.2016.07.065
%  [arXiv:1603.02913 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.07.065;%%
  %5 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016ewo}
%\bibitem{Khachatryan:2016ewo}
\item CMS Collaboration, ``Search for s channel single top quark production in pp collisions at $ \sqrt{s}=7 $ and 8 TeV'', JHEP {\bf 1609}, 027 (2016).
%  doi:10.1007/JHEP09(2016)027
%  [arXiv:1603.02555 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP09(2016)027;%%
  %32 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016mqs}
%\bibitem{Khachatryan:2016mqs}
\item CMS Collaboration, ``Measurement of the t-tbar production cross section in the e-mu channel in proton-proton collisions at sqrt(s) = 7 and 8 TeV'', JHEP {\bf 1608}, 029 (2016).
%  doi:10.1007/JHEP08(2016)029
%  [arXiv:1603.02303 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP08(2016)029;%%
  %84 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016olu}
%\bibitem{Khachatryan:2016olu}
\item CMS Collaboration, ``Search for heavy Majorana neutrinos in e$^{±}$e$^{±}$+ jets and e$^{±}$ $\mu^{±}$+ jets events in proton-proton collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1604}, 169 (2016).
%  doi:10.1007/JHEP04(2016)169
%  [arXiv:1603.02248 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP04(2016)169;%%
  %33 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016pev}
%\bibitem{Khachatryan:2016pev}
\item CMS Collaboration, ``Measurement of the differential cross section and charge asymmetry for inclusive $\mathrm {p}\mathrm {p}\rightarrow \mathrm {W}^{\pm }+X$ production at ${\sqrt{s}} = 8$ TeV'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 8, 469 (2016).
%  doi:10.1140/epjc/s10052-016-4293-4
%  [arXiv:1603.01803 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4293-4;%%
  %42 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016oia}
%\bibitem{Khachatryan:2016oia}
\item CMS Collaboration, ``Search for direct pair production of supersymmetric top quarks decaying to all-hadronic final states in pp collisions at $\sqrt{s} = 8\;\text {TeV} $'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 8, 460 (2016).
%  doi:10.1140/epjc/s10052-016-4292-5
%  [arXiv:1603.00765 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4292-5;%%
  %30 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016yzq}
%\bibitem{Khachatryan:2016yzq}
\item CMS Collaboration, ``Measurements of the $\mathrm{t}\overline{\mathrm{t}}$ production cross section in lepton+jets final states in pp collisions at 8 $\,\text {TeV}$ and ratio of 8 to 7  $\,\text {TeV}$ cross sections'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 1, 15 (2017)
%  doi:10.1140/epjc/s10052-016-4504-z
%  [arXiv:1602.09024 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4504-z;%%
  %31 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016hns}
%\bibitem{Khachatryan:2016hns}
\item CMS Collaboration, ``Search for supersymmetry in electroweak production with photons and large missing transverse energy in pp collisions at $\sqrt s = 8$ TeV'', Phys.\ Lett.\ B {\bf 759}, 479 (2016).
%  doi:10.1016/j.physletb.2016.05.088
%  [arXiv:1602.08772 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.05.088;%%
  %13 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016cfa}
%\bibitem{Khachatryan:2016cfa}
\item CMS Collaboration, ``Search for heavy resonances decaying to two Higgs bosons in final states containing four b quarks'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 7, 371 (2016).
%  doi:10.1140/epjc/s10052-016-4206-6
%  [arXiv:1602.08762 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4206-6;%%
  %29 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016yro}
%\bibitem{Khachatryan:2016yro}
\item CMS Collaboration, ``Measurement of the $ \mathrm{ Z } \gamma \rightarrow \nu \bar{\nu} \gamma$ production cross section in pp collisions at $\sqrt{s}=$ 8 TeV and limits on anomalous $ \mathrm{ ZZ } \gamma$ and $ \mathrm{Z} \gamma \gamma$ trilinear gauge boson couplings'', Phys.\ Lett.\ B {\bf 760}, 448 (2016).
%  doi:10.1016/j.physletb.2016.06.080
%  [arXiv:1602.07152 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.06.080;%%
  %11 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016kdk}
%\bibitem{Khachatryan:2016kdk}
\item CMS Collaboration, ``Search for supersymmetry in the multijet and missing transverse momentum final state in pp collisions at 13 TeV'', Phys.\ Lett.\ B {\bf 758}, 152 (2016).
%  doi:10.1016/j.physletb.2016.05.002
%  [arXiv:1602.06581 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.05.002;%%
  %61 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016hkr}
%\bibitem{Khachatryan:2016hkr}
\item CMS Collaboration, ``Measurement of dijet azimuthal decorrelation in pp collisions at $\sqrt{s}=8\,\mathrm{TeV} $'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 10, 536 (2016).
%  doi:10.1140/epjc/s10052-016-4346-8
%  [arXiv:1602.04384 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4346-8;%%
  %11 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016ycy}
%\bibitem{Khachatryan:2016ycy}
\item CMS Collaboration, ``Search for R-parity violating decays of a top squark in proton-proton collisions at $\sqrt{s}$ = 8 TeV'', Phys.\ Lett.\ B {\bf 760}, 178 (2016).
%  doi:10.1016/j.physletb.2016.06.039
%  [arXiv:1602.04334 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.06.039;%%
  %5 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016tnr}
%\bibitem{Khachatryan:2016tnr}
\item CMS Collaboration, ``Combined search for anomalous pseudoscalar HVV couplings in VH(H $\to b \bar b$) production and H $\to$ VV decay'', Phys.\ Lett.\ B {\bf 759}, 672 (2016).
%  doi:10.1016/j.physletb.2016.06.004
%  [arXiv:1602.04305 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.06.004;%%
  %27 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016pup}
%\bibitem{Khachatryan:2016pup}
\item CMS Collaboration, ``Search for direct pair production of scalar top quarks in the single- and dilepton channels in proton-proton collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1607}, 027 (2016), Erratum: [JHEP {\bf 1609}, 056 (2016)].
%  doi:10.1007/JHEP07(2016)027, 10.1007/JHEP09(2016)056
%  [arXiv:1602.03169 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP07(2016)027, 10.1007/JHEP09(2016)056;%%
  %34 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016zcu}
%\bibitem{Khachatryan:2016zcu}
\item CMS Collaboration, ``Search for supersymmetry in pp collisions at sqrt(s) = 8 TeV in final states with boosted W bosons and b jets using razor variables'', Phys.\ Rev.\ D {\bf 93}, no. 9, 092009 (2016).
%  doi:10.1103/PhysRevD.93.092009
%  [arXiv:1602.02917 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.93.092009;%%
  %10 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016udy}
%\bibitem{Khachatryan:2016udy}
\item CMS Collaboration, ``Azimuthal decorrelation of jets widely separated in rapidity in pp collisions at $ \sqrt{s}=7 $ TeV'', JHEP {\bf 1608}, 139 (2016).
%  doi:10.1007/JHEP08(2016)139
%  [arXiv:1601.06713 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP08(2016)139;%%
  %27 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016yji}
%\bibitem{Khachatryan:2016yji}
\item CMS Collaboration, ``Search for massive WH resonances decaying into the $\ell \nu \mathrm{b} \overline{\mathrm{b}} $ final state at $\sqrt{s}=8$ $~\text {TeV}$'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 5, 237 (2016).
%  doi:10.1140/epjc/s10052-016-4067-z
%  [arXiv:1601.06431 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4067-z;%%
  %37 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016yte}
%\bibitem{Khachatryan:2016yte}
\item CMS Collaboration, ``Forward–backward asymmetry of Drell–Yan lepton pairs in pp collisions at $\sqrt{s} = 8$ $\,\mathrm{TeV}$'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 6, 325 (2016).
%  doi:10.1140/epjc/s10052-016-4156-z
%  [arXiv:1601.04768 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4156-z;%%
  %16 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016xdg}
%\bibitem{Khachatryan:2016xdg}
\item CMS Collaboration, ``Measurement of inclusive jet production and nuclear modifications in pPb collisions at $\sqrt{s_{_\mathrm {NN}}} =$ 5.02 TeV'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 7, 372 (2016).
%  doi:10.1140/epjc/s10052-016-4205-7
%  [arXiv:1601.02001 [nucl-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4205-7;%%
  %16 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016xws}
%\bibitem{Khachatryan:2016xws}
\item CMS Collaboration, ``Measurements of t t-bar spin correlations and top quark polarization using dilepton final states in pp collisions at sqrt(s) = 8 TeV'', Phys.\ Rev.\ D {\bf 93}, no. 5, 052007 (2016).
%  doi:10.1103/PhysRevD.93.052007
%  [arXiv:1601.01107 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.93.052007;%%
  %32 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016erx}
%\bibitem{Khachatryan:2016erx}
\item CMS Collaboration, ``Correlations between jets and charged particles in PbPb and pp collisions at $ \sqrt{s_{\mathrm{NN}}}=2.76 $ TeV'', JHEP {\bf 1602}, 156 (2016).
%  doi:10.1007/JHEP02(2016)156
%  [arXiv:1601.00079 [nucl-ex]].
  %%CITATION = doi:10.1007/JHEP02(2016)156;%%
  %31 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015yvw}
%\bibitem{Khachatryan:2015yvw}
\item CMS Collaboration, ``Measurement of differential and integrated fiducial cross sections for Higgs boson production in the four-lepton decay channel in pp collisions at $ \sqrt{s}=7 $ and 8 TeV'', JHEP {\bf 1604}, 005 (2016).
%  doi:10.1007/JHEP04(2016)005
%  [arXiv:1512.08377 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP04(2016)005;%%
  %47 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015pot}
%\bibitem{Khachatryan:2015pot}
\item CMS Collaboration, ``Search for supersymmetry in events with soft leptons, low jet multiplicity, and missing transverse energy in proton–proton collisions at $\sqrt{s}$=8 TeV'', Phys.\ Lett.\ B {\bf 759}, 9 (2016).
%  doi:10.1016/j.physletb.2016.05.033
%  [arXiv:1512.08002 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.05.033;%%
  %36 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015pzs}
%\bibitem{Khachatryan:2015pzs}
\item CMS Collaboration, ``Study of Z boson production in pPb collisions at $\sqrt {s_{NN}} = 5.02$ TeV'', Phys.\ Lett.\ B {\bf 759}, 36 (2016).
%  doi:10.1016/j.physletb.2016.05.044
%  [arXiv:1512.06461 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.05.044;%%
  %27 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015luy}
%\bibitem{Khachatryan:2015luy}
\item CMS Collaboration, ``Measurement of the inclusive jet cross section in pp collisions at $\sqrt{s} = 2.76\,\text {TeV}$'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 5, 265 (2016).
%  doi:10.1140/epjc/s10052-016-4083-z
%  [arXiv:1512.06212 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4083-z;%%
  %16 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015dcf}
%\bibitem{Khachatryan:2015dcf}
\item CMS Collaboration, ``Search for narrow resonances decaying to dijets in proton-proton collisions at $\sqrt(s) =$ 13 TeV'', Phys.\ Rev.\ Lett.\  {\bf 116}, no. 7, 071801 (2016).
%  doi:10.1103/PhysRevLett.116.071801
%  [arXiv:1512.01224 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevLett.116.071801;%%
  %143 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015pea}
%\bibitem{Khachatryan:2015pea}
\item CMS Collaboration, ``Event generator tunes obtained from underlying event and multiparton scattering measurements'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 3, 155 (2016).
%  doi:10.1140/epjc/s10052-016-3988-x
%  [arXiv:1512.00815 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-3988-x;%%
  %249 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015bbl}
%\bibitem{Khachatryan:2015bbl}
\item CMS Collaboration, ``Search for dark matter and unparticles produced in association with a Z boson in proton-proton collisions at $\sqrt s=$ 8 TeV'', Phys.\ Rev.\ D {\bf 93}, no. 5, 052011 (2016).
%  doi:10.1103/PhysRevD.93.052011
%  [arXiv:1511.09375 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.93.052011;%%
  %30 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015tzo}
%\bibitem{Khachatryan:2015tzo}
\item CMS Collaboration, ``Measurement of spin correlations in $t\bar{t}$ production using the matrix element method in the muon+jets final state in pp collisions at $\sqrt{s} =$ 8 TeV'', Phys.\ Lett.\ B {\bf 758}, 321 (2016).
%  doi:10.1016/j.physletb.2016.05.005
%  [arXiv:1511.06170 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.05.005;%%
  %17 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015att}
%\bibitem{Khachatryan:2015att}
\item CMS Collaboration, ``Search for anomalous single top quark production in association with a photon in pp collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1604}, 035 (2016).
%  doi:10.1007/JHEP04(2016)035
%  [arXiv:1511.03951 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP04(2016)035;%%
  %41 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015baw}
%\bibitem{Khachatryan:2015baw}
\item CMS Collaboration, ``Search for a low-mass pseudoscalar Higgs boson produced in association with a $b\bar{b}$ pair in pp collisions at $\sqrt{s} =$ 8 TeV'', Phys.\ Lett.\ B {\bf 758}, 296 (2016).
%  doi:10.1016/j.physletb.2016.05.003
%  [arXiv:1511.03610 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.05.003;%%
  %25 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015dzz}
%\bibitem{Khachatryan:2015dzz}
\item CMS Collaboration, ``Measurement of top quark polarisation in t-channel single top quark production'', JHEP {\bf 1604}, 073 (2016).
%  doi:10.1007/JHEP04(2016)073
%  [arXiv:1511.02138 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP04(2016)073;%%
  %30 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015scf}
%\bibitem{Khachatryan:2015scf}
\item CMS Collaboration, ``Search for excited leptons in proton-proton collisions at sqrt(s) = 8 TeV'', JHEP {\bf 1603}, 125 (2016).
%  doi:10.1007/JHEP03(2016)125
%  [arXiv:1511.01407 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP03(2016)125;%%
  %16 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015dfa}
%\bibitem{Khachatryan:2015dfa}
\item CMS Collaboration, ``Reconstruction and identification of $\tau$ lepton decays to hadrons and v$_\tau$ at CMS'', JINST {\bf 11}, no. 01, P01019 (2016).
%  doi:10.1088/1748-0221/11/01/P01019
%  [arXiv:1510.07488 [physics.ins-det]].
  %%CITATION = doi:10.1088/1748-0221/11/01/P01019;%%
  %99 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015nba}
%\bibitem{Khachatryan:2015nba}
\item CMS Collaboration, ``Search for a very light NMSSM Higgs boson produced in decays of the 125 GeV scalar boson and decaying into $\tau$ leptons in pp collisions at $\sqrt{s}=8$ TeV'', JHEP {\bf 1601}, 079 (2016).
%  doi:10.1007/JHEP01(2016)079
%  [arXiv:1510.06534 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP01(2016)079;%%
  %28 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015uqb}
%\bibitem{Khachatryan:2015uqb}
\item CMS Collaboration, ``Measurement of the top quark pair production cross section in proton-proton collisions at $\sqrt(s) =$ 13 TeV'', Phys.\ Rev.\ Lett.\  {\bf 116}, no. 5, 052002 (2016).
%  doi:10.1103/PhysRevLett.116.052002
%  [arXiv:1510.05302 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevLett.116.052002;%%
  %65 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015uua}
%\bibitem{Khachatryan:2015uua}
\item CMS Collaboration, ``Search for a light charged Higgs boson decaying to $ \mathrm{c}\overline{\mathrm{s}} $ in pp collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1512}, 178 (2015).
%  doi:10.1007/JHEP12(2015)178
%  [arXiv:1510.04252 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP12(2015)178;%%
  %40 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015sva}
%\bibitem{Khachatryan:2015sva}
\item CMS Collaboration, ``Transverse momentum spectra of inclusive b jets in pPb collisions at $\sqrt{s_{NN}} = $ 5.02 TeV'', Phys.\ Lett.\ B {\bf 754}, 59 (2016).
%  doi:10.1016/j.physletb.2016.01.010
%  [arXiv:1510.03373 [nucl-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.01.010;%%
  %32 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015mva}
%\bibitem{Khachatryan:2015mva}
\item CMS Collaboration, ``Measurement of $\mathrm {t}\overline{\mathrm {t}}$ production with additional jet activity, including $\mathrm {b}$ quark jets, in the dilepton decay channel using pp collisions at $\sqrt{s} =$ 8 TeV'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 7, 379 (2016).
%  doi:10.1140/epjc/s10052-016-4105-x
%  [arXiv:1510.03072 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4105-x;%%
  %48 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015lva}
%\bibitem{Khachatryan:2015lva}
\item CMS Collaboration, ``Measurement of long-range near-side two-particle angular correlations in pp collisions at $\sqrt s =$13 TeV'', Phys.\ Rev.\ Lett.\  {\bf 116}, no. 17, 172302 (2016).
%  doi:10.1103/PhysRevLett.116.172302
%  [arXiv:1510.03068 [nucl-ex]].
  %%CITATION = doi:10.1103/PhysRevLett.116.172302;%%
  %83 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015tha}
%\bibitem{Khachatryan:2015tha}
\item CMS Collaboration, ``Searches for a heavy scalar boson H decaying to a pair of 125 GeV Higgs bosons hh or for a heavy pseudoscalar boson A decaying to Zh, in the final states with $h \to \tau \tau$'', Phys.\ Lett.\ B {\bf 755}, 217 (2016).
%  doi:10.1016/j.physletb.2016.01.056
%  [arXiv:1510.01181 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.01.056;%%
  %69 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015sha}
%\bibitem{Khachatryan:2015sha}
\item CMS Collaboration, ``Observation of top quark pairs produced in association with a vector boson in pp collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1601}, 096 (2016).
%  doi:10.1007/JHEP01(2016)096
%  [arXiv:1510.01131 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP01(2016)096;%%
  %60 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015lha}
%\bibitem{Khachatryan:2015lha}
\item CMS Collaboration, ``Measurement of transverse momentum relative to dijet systems in PbPb and pp collisions at $ \sqrt{s_{\mathrm{NN}}}=2.76 $ TeV'', JHEP {\bf 1601}, 006 (2016).
%  doi:10.1007/JHEP01(2016)006
%  [arXiv:1509.09029 [nucl-ex]].
  %%CITATION = doi:10.1007/JHEP01(2016)006;%%
  %50 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015ota}
%\bibitem{Khachatryan:2015ota}
\item CMS Collaboration, ``Search for the associated production of a Higgs boson with a single top quark in proton-proton collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1606}, 177 (2016).
%  doi:10.1007/JHEP06(2016)177
%  [arXiv:1509.08159 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP06(2016)177;%%
  %26 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015mta}
%\bibitem{Khachatryan:2015mta}
\item CMS Collaboration, ``Search for the production of an excited bottom quark decaying to $tW$ in proton-proton collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1601}, 166 (2016).
%  doi:10.1007/JHEP01(2016)166
%  [arXiv:1509.08141 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP01(2016)166;%%
  %15 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015fwh}
%\bibitem{Khachatryan:2015fwh}
\item CMS Collaboration, ``Measurement of the $\mathrm{t}\overline{{\mathrm{t}}}$ production cross section in the all-jets final state in pp collisions at $\sqrt{s}=8$ $\,\text {TeV}$'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 3, 128 (2016).
%  doi:10.1140/epjc/s10052-016-3956-5
%  [arXiv:1509.06076 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-3956-5;%%
  %36 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015edz}
%\bibitem{Khachatryan:2015edz}
\item CMS Collaboration, ``Search for $W' \to tb$ in proton-proton collisions at $\sqrt{s} = $ 8 TeV'', JHEP {\bf 1602}, 122 (2016).
%  doi:10.1007/JHEP02(2016)122
%  [arXiv:1509.06051 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP02(2016)122;%%
  %22 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015oba}
%\bibitem{Khachatryan:2015oba}
\item CMS Collaboration, ``Search for vector-like charge 2/3 T quarks in proton-proton collisions at sqrt(s) = 8 TeV'', Phys.\ Rev.\ D {\bf 93}, no. 1, 012003 (2016).
%  doi:10.1103/PhysRevD.93.012003
%  [arXiv:1509.04177 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.93.012003;%%
  %113 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015hba}
%\bibitem{Khachatryan:2015hba}
\item CMS Collaboration, ``Measurement of the top quark mass using proton-proton data at ${\sqrt{(s)}}$ = 7 and 8 TeV'', Phys.\ Rev.\ D {\bf 93}, no. 7, 072004 (2016).
%  doi:10.1103/PhysRevD.93.072004
%  [arXiv:1509.04044 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.93.072004;%%
  %136 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015zaa}
%\bibitem{Khachatryan:2015zaa}
\item CMS Collaboration, ``Measurement of the inelastic cross section in proton–lead collisions at $\sqrt {s_{NN}}=$ 5.02 TeV'', Phys.\ Lett.\ B {\bf 759}, 641 (2016).
%  doi:10.1016/j.physletb.2016.06.027
%  [arXiv:1509.03893 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.06.027;%%
  %10 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015qda}
%\bibitem{Khachatryan:2015qda}
\item CMS Collaboration, ``Search for single production of scalar leptoquarks in proton-proton collisions at $\sqrt{s} = 8$ $TeV$'', Phys.\ Rev.\ D {\bf 93}, no. 3, 032005 (2016), Erratum: [Phys.\ Rev.\ D {\bf 95}, no. 3, 039906 (2017)].
%  doi:10.1103/PhysRevD.95.039906, 10.1103/PhysRevD.93.032005
%  [arXiv:1509.03750 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.95.039906, 10.1103/PhysRevD.93.032005;%%
  %22 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015vaa}
%\bibitem{Khachatryan:2015vaa}
\item CMS Collaboration, ``Search for pair production of first and second generation leptoquarks in proton-proton collisions at $\sqrt{s}$ = 8 TeV'', Phys.\ Rev.\ D {\bf 93}, no. 3, 032004 (2016).
%  doi:10.1103/PhysRevD.93.032004
%  [arXiv:1509.03744 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.93.032004;%%
  %49 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015rxa}
%\bibitem{Khachatryan:2015rxa}
\item CMS Collaboration, ``Measurement of differential cross sections for Higgs boson production in the diphoton decay channel in pp collisions at $\sqrt{s}=8\,\text {TeV} $'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 1, 13 (2016).
%  doi:10.1140/epjc/s10052-015-3853-3
%  [arXiv:1508.07819 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-015-3853-3;%%
  %63 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015qxa}
%\bibitem{Khachatryan:2015qxa}
\item CMS Collaboration, ``Search for a charged Higgs boson in pp collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1511}, 018 (2015).
%  doi:10.1007/JHEP11(2015)018
%  [arXiv:1508.07774 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP11(2015)018;%%
  %98 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015kxa}
%\bibitem{Khachatryan:2015kxa}
\item CMS Collaboration, ``Search for supersymmetry in the vector-boson fusion topology in proton-proton collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1511}, 189 (2015).
%  doi:10.1007/JHEP11(2015)189
%  [arXiv:1508.07628 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP11(2015)189;%%
  %14 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015uja}
%\bibitem{Khachatryan:2015uja}
\item CMS Collaboration, ``Study of B Meson Production in p$+$Pb Collisions at $\sqrt{s_{NN}}=5.02$ TeV Using Exclusive Hadronic Decays'', Phys.\ Rev.\ Lett.\  {\bf 116}, no. 3, 032301 (2016).
%  doi:10.1103/PhysRevLett.116.032301
%  [arXiv:1508.06678 [nucl-ex]].
  %%CITATION = doi:10.1103/PhysRevLett.116.032301;%%
  %39 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015pua}
%\bibitem{Khachatryan:2015pua}
\item CMS Collaboration, ``Search for W' decaying to tau lepton and neutrino in proton-proton collisions at $\sqrt(s) =$ 8 TeV'', Phys.\ Lett.\ B {\bf 755}, 196 (2016).
%  doi:10.1016/j.physletb.2016.02.002
%  [arXiv:1508.04308 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.02.002;%%
  %15 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015mna}
%\bibitem{Khachatryan:2015mna}
\item CMS Collaboration, ``Measurement of the charge asymmetry in top quark pair production in pp collisions at $\sqrt(s) =$ 8 TeV using a template method'', Phys.\ Rev.\ D {\bf 93}, no. 3, 034014 (2016).
%  doi:10.1103/PhysRevD.93.034014
%  [arXiv:1508.03862 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.93.034014;%%
  %27 citations counted in INSPIRE as of 12 Jan 2018

%\cite{CMS:2015ooa}
%\bibitem{CMS:2015ooa}
\item CMS Collaboration, ``Search for neutral MSSM Higgs bosons decaying to $\mu^{+} \mu^{-}$ in pp collisions at $ \sqrt{s} =$ 7 and 8 TeV'', Phys.\ Lett.\ B {\bf 752}, 221 (2016).
%  doi:10.1016/j.physletb.2015.11.042
%  [arXiv:1508.01437 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2015.11.042;%%
  %19 citations counted in INSPIRE as of 12 Jan 2018

%\cite{CMS:2015loa}
%\bibitem{CMS:2015loa}
\item CMS Collaboration, ``Search for supersymmetry in events with a photon, a lepton, and missing transverse momentum in pp collisions at $\sqrt s=$ 8 TeV'', Phys.\ Lett.\ B {\bf 757}, 6 (2016).
%  doi:10.1016/j.physletb.2016.03.039
%  [arXiv:1508.01218 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.03.039;%%
  %8 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015isa}
%\bibitem{Khachatryan:2015isa}
\item CMS Collaboration, ``Angular analysis of the decay $B^0 \to K^{*0} \mu^+ \mu^-$ from pp collisions at $\sqrt  s = 8$ TeV'', Phys.\ Lett.\ B {\bf 753}, 424 (2016).
%  doi:10.1016/j.physletb.2015.12.020
%  [arXiv:1507.08126 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2015.12.020;%%
  %53 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015nza}
%\bibitem{Khachatryan:2015nza}
\item CMS Collaboration, ``Measurement of the CP-violating weak phase $\phi_s$ and the decay width difference $\Delta \Gamma_s$ using the B$_s^0 \to J/\psi\phi$(1020) decay channel in pp collisions at $\sqrt{s}=$ 8 TeV'', Phys.\ Lett.\ B {\bf 757}, 97 (2016).
%  doi:10.1016/j.physletb.2016.03.046
%  [arXiv:1507.07527 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.03.046;%%
  %37 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015jza}
%\bibitem{Khachatryan:2015jza}
\item CMS Collaboration, ``Measurement of the underlying event activity using charged-particle jets in proton-proton collisions at sqrt(s) = 2.76 TeV'', JHEP {\bf 1509}, 137 (2015).
%  doi:10.1007/JHEP09(2015)137
%  [arXiv:1507.07229 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP09(2015)137;%%
  %15 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015gza}
%\bibitem{Khachatryan:2015gza}
\item CMS Collaboration, ``Search for pair-produced vectorlike B quarks in proton-proton collisions at $\sqrt{s}$=8 TeV'', Phys.\ Rev.\ D {\bf 93}, no. 11, 112009 (2016).
%  doi:10.1103/PhysRevD.93.112009
%  [arXiv:1507.07129 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.93.112009;%%
  %72 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015mma}
%\bibitem{Khachatryan:2015mma}
\item CMS Collaboration, ``Limits on the Higgs boson lifetime and width from its decay to four charged leptons'', Phys.\ Rev.\ D {\bf 92}, no. 7, 072010 (2015).
%  doi:10.1103/PhysRevD.92.072010
%  [arXiv:1507.06656 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.92.072010;%%
  %43 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015jna}
%\bibitem{Khachatryan:2015jna}
\item CMS Collaboration, ``Pseudorapidity distribution of charged hadrons in proton-proton collisions at $\sqrt{s}$ = 13 TeV'', Phys.\ Lett.\ B {\bf 751}, 143 (2015).
%  doi:10.1016/j.physletb.2015.10.004
%  [arXiv:1507.05915 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2015.10.004;%%
  %48 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015sga}
%\bibitem{Khachatryan:2015sga}
\item CMS Collaboration, ``Measurement of the ${{\mathrm{W} }^{+} }\mathrm{W}^{-} $ cross section in pp collisions at $\sqrt{s} =$ 8 TeV and limits on anomalous gauge couplings'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 7, 401 (2016).
%  doi:10.1140/epjc/s10052-016-4219-1
%  [arXiv:1507.03268 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4219-1;%%
  %60 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015oga}
%\bibitem{Khachatryan:2015oga}
\item CMS Collaboration, ``Inclusive and differential measurements of the $t\overline{t}$ charge asymmetry in pp collisions at $\sqrt{s} =$ 8 TeV'', Phys.\ Lett.\ B {\bf 757}, 154 (2016).
%  doi:10.1016/j.physletb.2016.03.060
%  [arXiv:1507.03119 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.03.060;%%
  %31 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015lga}
%\bibitem{Khachatryan:2015lga}
\item CMS Collaboration, ``Search for a Higgs boson decaying into $\gamma^* \gamma \to \ell \ell \gamma$ with low dilepton mass in pp collisions at $\sqrt s = $ 8 TeV'', Phys.\ Lett.\ B {\bf 753}, 341 (2016).
%  doi:10.1016/j.physletb.2015.12.039
%  [arXiv:1507.03031 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2015.12.039;%%
  %13 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015exa}
%\bibitem{Khachatryan:2015exa}
\item CMS Collaboration, ``Search for supersymmetry with photons in pp collisions at $\sqrt{s}$=8 TeV'', Phys.\ Rev.\ D {\bf 92}, no. 7, 072006 (2015).
%  doi:10.1103/PhysRevD.92.072006
%  [arXiv:1507.02898 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.92.072006;%%
  %21 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015vta}
%\bibitem{Khachatryan:2015vta}
\item CMS Collaboration, ``Search for exotic decays of a Higgs boson into undetectable particles and one or more photons'', Phys.\ Lett.\ B {\bf 753}, 363 (2016).
%  doi:10.1016/j.physletb.2015.12.017
%  [arXiv:1507.00359 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2015.12.017;%%
  %15 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015tra}
%\bibitem{Khachatryan:2015tra}
\item CMS Collaboration, ``Search for neutral MSSM Higgs bosons decaying into a pair of bottom quarks'', JHEP {\bf 1511}, 071 (2015).
%  doi:10.1007/JHEP11(2015)071
%  [arXiv:1506.08329 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP11(2015)071;%%
  %52 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015sma}
%\bibitem{Khachatryan:2015sma}
\item CMS Collaboration, ``Search for resonant $t \bar t$ production in proton-proton collisions at $\sqrt s=$ 8 TeV'', Phys.\ Rev.\ D {\bf 93}, no. 1, 012001 (2016).
%  doi:10.1103/PhysRevD.93.012001
%  [arXiv:1506.03062 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.93.012001;%%
  %100 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015qba}
%\bibitem{Khachatryan:2015qba}
\item CMS Collaboration, ``Search for diphoton resonances in the mass range from 150 to 850 GeV in pp collisions at $\sqrt{s} =$ 8 TeV'', Phys.\ Lett.\ B {\bf 750}, 494 (2015).
%  doi:10.1016/j.physletb.2015.09.062
%  [arXiv:1506.02301 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2015.09.062;%%
  %141 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015bma}
%\bibitem{Khachatryan:2015bma}
\item CMS Collaboration, ``Search for a massive resonance decaying into a Higgs boson and a W or Z boson in hadronic final states in proton-proton collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1602}, 145 (2016).
%  doi:10.1007/JHEP02(2016)145
%  [arXiv:1506.01443 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP02(2016)145;%%
  %86 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015bnx}
%\bibitem{Khachatryan:2015bnx}
\item CMS Collaboration, ``Search for the standard model Higgs boson produced through vector boson fusion and decaying to $b \overline{b}$'', Phys.\ Rev.\ D {\bf 92}, no. 3, 032008 (2015).
%  doi:10.1103/PhysRevD.92.032008
%  [arXiv:1506.01010 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevD.92.032008;%%
  %54 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015wka}
%\bibitem{Khachatryan:2015wka}
\item CMS Collaboration, ``A search for pair production of new light bosons decaying into muons'', Phys.\ Lett.\ B {\bf 752}, 146 (2016).
%  doi:10.1016/j.physletb.2015.10.067
%  [arXiv:1506.00424 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2015.10.067;%%
  %50 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015jea}
%\bibitem{Khachatryan:2015jea}
\item CMS Collaboration, ``Search for neutral color-octet weak-triplet scalar particles in proton-proton collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1509}, 201 (2015).
%  doi:10.1007/JHEP09(2015)201
%  [arXiv:1505.08118 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP09(2015)201;%%
  %3 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015ira}
%\bibitem{Khachatryan:2015ira}
\item CMS Collaboration, ``Comparison of the Z/$\gamma$$^{*}$ + jets to $\gamma$ + jets cross sections in pp collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1510}, 128 (2015), Erratum: [JHEP {\bf 1604}, 010 (2016)].
%  doi:10.1007/JHEP04(2016)010, 10.1007/JHEP10(2015)128
%  [arXiv:1505.06520 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP04(2016)010, 10.1007/JHEP10(2015)128;%%
  %27 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015lba}
%\bibitem{Khachatryan:2015lba}
\item CMS Collaboration, ``Search for a pseudoscalar boson decaying into a Z boson and the 125 GeV Higgs boson in $\ell^+\ell^-b\overline{b}$ final states'', Phys.\ Lett.\ B {\bf 748}, 221 (2015).
%  doi:10.1016/j.physletb.2015.07.010
%  [arXiv:1504.04710 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2015.07.010;%%
  %66 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015cwa}
%\bibitem{Khachatryan:2015cwa}
\item CMS Collaboration, ``Search for a Higgs boson in the mass range from 145 to 1000 GeV decaying to a pair of W or Z bosons'', JHEP {\bf 1510}, 144 (2015).
%  doi:10.1007/JHEP10(2015)144
%  [arXiv:1504.00936 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP10(2015)144;%%
  %177 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015bsa}
%\bibitem{Khachatryan:2015bsa}
\item CMS Collaboration, ``Search for Third-Generation Scalar Leptoquarks in the t$\tau$ Channel in Proton-Proton Collisions at $\sqrt{s}$ = 8 TeV'', JHEP {\bf 1507}, 042 (2015), Erratum: [JHEP {\bf 1611}, 056 (2016)].
%  doi:10.1007/JHEP11(2016)056, 10.1007/JHEP07(2015)042
%  [arXiv:1503.09049 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP11(2016)056, 10.1007/JHEP07(2015)042;%%
  %40 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015wza}
%\bibitem{Khachatryan:2015wza}
\item CMS Collaboration, ``Searches for third-generation squark production in fully hadronic final states in proton-proton collisions at $ \sqrt{s} = 8$ TeV'', JHEP {\bf 1506}, 116 (2015).
%  doi:10.1007/JHEP06(2015)116
%  [arXiv:1503.08037 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP06(2015)116;%%
  %113 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015oea}
%\bibitem{Khachatryan:2015oea}
\item CMS Collaboration, ``Evidence for transverse momentum and pseudorapidity dependent event plane fluctuations in PbPb and pPb collisions'', Phys.\ Rev.\ C {\bf 92}, no. 3, 034911 (2015).
%  doi:10.1103/PhysRevC.92.034911
%  [arXiv:1503.01692 [nucl-ex]].
  %%CITATION = doi:10.1103/PhysRevC.92.034911;%%
  %82 citations counted in INSPIRE as of 12 Jan 2018  
  \end{enumerate}
\end{itemize}
