\chapter*{List of Publications/Conferences}
\markboth{}{}
\fontsize{11pt}{12pt}\selectfont

\section*{CMS Public Notes}% with Direct Contribution}
\begin{enumerate}
\item CMS Collaboration, ``Measurement of the differential Drell-Yan cross section in proton-proton collisions at 13 TeV'', {\bf CMS-PAS-SMP-16-009} (2016).
\end{enumerate}
%\noindent\makebox[\textwidth]{\rule{\textwidth}{1pt}}

\section*{CMS Analysis Notes}% with Direct Contribution}
\begin{enumerate}
\item R. Chawla {\it et al.}, ``Measurement of the differential DY cross section at $\sqrt{s}$ = 13 TeV'', {\bf CMS AN-2015/324} (2015).
\end{enumerate}
%\noindent\makebox[\textwidth]{\rule{\textwidth}{1pt}}

\section*{Papers in Refreed Journals}
\begin{enumerate}
\item R. Chawla and M. Kaur, ``Shifted Gompertz PDF for multipliciticies in high energy leptonic and hadronic collisions'', arXiv:1801.00278 [hep-ph].
\item R. Chawla {\it et al.}, ``Differential cross section measurement of the Drell-Yan process at 13 TeV proton-proton collisions with the CMS detector'', Springer Proc. Phys. {\bf 203} (2018) doi:10.1007/978-3-319-73171-1
\end{enumerate}
%\noindent\makebox[\textwidth]{\rule{\textwidth}{1pt}}

\section*{Papers presented in Conferences, Workshops and Symposiums}
\begin{enumerate}
\item R. Chawla {\it et al.}, ``Precision Measurements of Drell-Yan production'', {\bf SM@LHC 2017: Standard Model at the LHC 2017}, 2-5 May, 2017, Amsterdam, Netherlands.
\item R. Chawla {\it et al.}, ``Drell-Yan differential cross section measurement in pp collisions with the CMS detector'', {\bf 11$^{\textrm{th}}$ Chandigarh Science Congress, CHASCON 2017}, 9-11 March, 2017, Panjab University, Chandigarh, India.
\item R. Chawla {\it et al.}, ``Differential cross section measurement of the Drell-Yan process at 13 TeV proton-proton collisions with the CMS detector'', {\bf XXII DAE­-BRNS High Energy Physics Symposium 2016}, 12-16 December, 2016, Delhi, India.
\item R. Chawla {\it et al.}, ``Data Certification Report
'', {\bf CMS Week 2016}, 14-18 November, 2016, Mumbai, India.
\item R. Chawla {\it et al.}, ``Drell-Yan Differential Cross Section Measurement at $\sqrt{s}$ = 13 TeV with p-p collisions in the CMS Detector'', {\bf International Workshop on Frontiers in Electroweak Interactions of Leptons and Hadrons}, 2-6 November, 2016, Aligarh, India.
\item R. Chawla {\it et al.}, ``HCAL Back-End Upgradation at CMS Detector'', {\bf 9$^{\textrm{th}}$ Chandigarh Science Congress, CHASCON 2017}, 25-27 February, 2015, Panjab University, Chandigarh, India.
\end{enumerate}
%\noindent\makebox[\textwidth]{\rule{\textwidth}{1pt}}

\section*{Conferences, Schools and Workshops attended}
\begin{enumerate}
\item {\bf Workshop on Upgrade of the CMS Calorimeter}, 23-24 November, 2015, Tata Institute of Fundamental Research, Mumbai, India.
\item {\bf Workshop on High Performance Computing}, 16-17 March, 2015, Panjab University, Chandigarh, India.
\item {\bf IX SERC SCHOOL ON EXPERIMENTAL HIGH ENERGY PHYSICS}, 2-21 November, 2013, Indian Institute of Technology Madras, Chenai, India.
\item {\bf CMS Data Analysis School (CMSDAS)}, 7-11 November, 2013, Saha Institute of Nuclear Physics, Kolkata, India.
\end{enumerate}
%\noindent\makebox[\textwidth]{\rule{\textwidth}{1pt}}

\section*{CMS Publications}%\url{http://inspirehep.net/search?ln=en&ln=en&p=ridhi+chawla&of=hb&action_search=Search&sf=earliestdate&so=d&rm=&rg=250&sc=0}
\begin{enumerate}
%\cite{Sirunyan:2017ret}
%\bibitem{Sirunyan:2017ret} 
\item CMS Collaboration, ``Observation of electroweak production of same-sign W boson pairs in the two jet and two same-sign lepton final state in proton-proton collisions at $\sqrt{s} = $ 13 TeV'', Phys.\ Rev.\ Lett.\  {\bf 120}, no. 8, 081801 (2018).
  %doi:10.1103/PhysRevLett.120.081801
  %[arXiv:1709.05822 [hep-ex]].
  %%CITATION = doi:10.1103/PhysRevLett.120.081801;%%
  %6 citations counted in INSPIRE as of 01 Mar 2018

%\cite{Sirunyan:2017fvv}
%\bibitem{Sirunyan:2017fvv}
\item CMS Collaboration, ``Measurement of vector boson scattering and constraints on anomalous quartic couplings from events with four leptons and two jets in proton-proton collisions at $\sqrt{s}=$ 13 TeV'', Phys.\ Lett.\ B {\bf 774}, 682 (2017).
  %doi:10.1016/j.physletb.2017.10.020
  %[arXiv:1708.02812 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.10.020;%%
  %2 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017wgx}
%\bibitem{Sirunyan:2017wgx}
\item CMS Collaboration, ``Measurement of the differential cross sections for the associated production of a $W$ boson and jets in proton-proton collisions at $\sqrt{s}=13$ TeV'', Phys.\ Rev.\ D {\bf 96}, no. 7, 072005 (2017).
  %doi:10.1103/PhysRevD.96.072005
  %[arXiv:1707.05979 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevD.96.072005;%%
  %5 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017tyr}
%\bibitem{Sirunyan:2017tyr}
\item CMS Collaboration, ``Measurements of jet charge with dijet events in pp collisions at $\sqrt{s}$ = 8 TeV'', JHEP {\bf 1710}, 131 (2017).
  %doi:10.1007/JHEP10(2017)131
  %[arXiv:1706.05868 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP10(2017)131;%%

%\cite{Sirunyan:2017skj}
%\bibitem{Sirunyan:2017skj}
\item CMS Collaboration, ``Measurement of the triple-differential dijet cross section in proton-proton collisions at $\sqrt{s}=8\,\text {TeV} $ and constraints on parton distribution functions'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 11, 746 (2017).
  %doi:10.1140/epjc/s10052-017-5286-7
  %[arXiv:1705.02628 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-5286-7;%%
  %7 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017lvq}
%\bibitem{Sirunyan:2017lvq}
\item CMS Collaboration, ``Measurements of the pp $\to W\gamma\gamma$ and pp $\to Z\gamma\gamma$ cross sections and limits on anomalous quartic gauge couplings at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1710}, 072 (2017).
  %doi:10.1007/JHEP10(2017)072
  %[arXiv:1704.00366 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP10(2017)072;%%
  %5 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Sirunyan:2017bey}
%\bibitem{Sirunyan:2017bey}
\item CMS Collaboration, ``Search for anomalous couplings in boosted $\mathrm{ WW/WZ }\to\ell\nu\mathrm{ q \bar{q} }$ production in proton-proton collisions at $\sqrt{s} =$ 8 TeV'', Phys.\ Lett.\ B {\bf 772}, 21 (2017).
  %doi:10.1016/j.physletb.2017.06.009
  %[arXiv:1703.06095 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.06.009;%%
  %10 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2017jub}
%\bibitem{Khachatryan:2017jub}
\item CMS Collaboration, ``Measurement of the cross section for electroweak production of Z$\gamma$ in association with two jets and constraints on anomalous quartic gauge couplings in proton-proton collisions at $\sqrt{s} = 8$ TeV'', Phys.\ Lett.\ B {\bf 770}, 380 (2017).
  %doi:10.1016/j.physletb.2017.04.071
  %[arXiv:1702.03025 [hep-ex]].
  %%CITATION = %doi:10.1016/j.physletb.2017.04.071;%%
  %5 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016vif}
%\bibitem{Khachatryan:2016vif}
\item CMS Collaboration, ``Measurement of electroweak-induced production of W$\gamma$ with two jets in pp collisions at $ \sqrt{s}=8 $ TeV and constraints on anomalous quartic gauge couplings'', JHEP {\bf 1706}, 106 (2017).
  %doi:10.1007/JHEP06(2017)106
  %[arXiv:1612.09256 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP06(2017)106;%%
  %4 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016iob}
%\bibitem{Khachatryan:2016iob}
\item CMS Collaboration, ``Measurements of the associated production of a Z boson and b jets in pp collisions at ${\sqrt{s}} = 8\,\text {TeV} $'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 11, 751 (2017).
  %doi:10.1140/epjc/s10052-017-5140-y
  %[arXiv:1611.06507 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-5140-y;%%
  %7 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016crw}
%\bibitem{Khachatryan:2016crw}
\item CMS Collaboration, ``Measurements of differential production cross sections for a Z boson in association with jets in pp collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1704}, 022 (2017).
  %doi:10.1007/JHEP04(2017)022
  %[arXiv:1611.03844 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP04(2017)022;%%
  %10 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016fue}
%\bibitem{Khachatryan:2016fue}
\item CMS Collaboration, ``Measurements of differential cross sections for associated production of a W boson and jets in proton-proton collisions at $\sqrt{s} =$ 8 TeV'', Phys.\ Rev.\ D {\bf 95}, 052002 (2017).
  %doi:10.1103/PhysRevD.95.052002
  %[arXiv:1610.04222 [hep-ex]].
  %%CITATION = %doi:10.1103/PhysRevD.95.052002;%%
  %10 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016poo}
%\bibitem{Khachatryan:2016poo}
\item CMS Collaboration, ``Measurement of the WZ production cross section in pp collisions at $\sqrt{s} = 7$ and 8 $\,\text{TeV}$ and search for anomalous triple gauge couplings at $\sqrt{s} = 8\,\text{TeV} $'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 4, 236 (2017).
  %doi:10.1140/epjc/s10052-017-4730-z
  %[arXiv:1609.05721 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-017-4730-z;%%
  %12 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016mlc}
%\bibitem{Khachatryan:2016mlc}
\item CMS Collaboration, ``Measurement and QCD analysis of double-differential inclusive jet cross sections in pp collisions at $ \sqrt{s}=8 $ TeV and cross section ratios to 2.76 and 7 TeV'', JHEP {\bf 1703}, 156 (2017).
  %doi:10.1007/JHEP03(2017)156
  %[arXiv:1609.05331 [hep-ex]].
  %%CITATION = %doi:10.1007/JHEP03(2017)156;%%
  %31 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016ipq}
%\bibitem{Khachatryan:2016ipq}
\item CMS Collaboration, ``Measurement of the production cross section of a W boson in association with two b jets in pp collisions at $\sqrt{s} = 8{\,\mathrm{{TeV}}} $'', Eur.\ Phys.\ J.\ C {\bf 77}, no. 2, 92 (2017).
  %doi:10.1140/epjc/s10052-016-4573-z
  %[arXiv:1608.07561 [hep-ex]].
  %%CITATION = %doi:10.1140/epjc/s10052-016-4573-z;%%
  %10 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016txa}
%\bibitem{Khachatryan:2016txa} 
\item CMS Collaboration, ``Measurement of the ZZ production cross section and Z $\to \ell^+\ell^-\ell'^+\ell'^-$ branching fraction in pp collisions at $\sqrt s$=13 TeV'', Phys.\ Lett.\ B {\bf 763}, 280 (2016), Erratum: [Phys.\ Lett.\ B {\bf 772}, 884 (2017)].
%  doi:10.1016/j.physletb.2017.09.030, 10.1016/j.physletb.2016.10.054
%  [arXiv:1607.08834 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2017.09.030, 10.1016/j.physletb.2016.10.054;%%
  %28 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016tgp}
%\bibitem{Khachatryan:2016tgp} 
\item CMS Collaboration, ``Measurement of the WZ production cross section in pp collisions at $\sqrt(s) =$ 13 TeV'', Phys.\ Lett.\ B {\bf 766}, 268 (2017)
%  doi:10.1016/j.physletb.2017.01.011
%  [arXiv:1607.06943 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2017.01.011;%%
  %34 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016qkk}
%\bibitem{Khachatryan:2016qkk} 
\item CMS Collaboration, ``Measurement of electroweak production of a W boson and two forward jets in proton-proton collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1611}, 147 (2016).
%  doi:10.1007/JHEP11(2016)147
%  [arXiv:1607.06975 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP11(2016)147;%%
  %6 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016nbe}
%\bibitem{Khachatryan:2016nbe} 
\item CMS Collaboration, ``Measurement of the transverse momentum spectra of weak vector bosons produced in proton-proton collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1702}, 096 (2017)
%  doi:10.1007/JHEP02(2017)096
%  [arXiv:1606.05864 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP02(2017)096;%%
  %14 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016wdh}
%\bibitem{Khachatryan:2016wdh} 
\item CMS Collaboration, ``Measurement of the double-differential inclusive jet cross section in proton–proton collisions at $\sqrt{s} = 13\,\text {TeV} $'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 8, 451 (2016).
%  doi:10.1140/epjc/s10052-016-4286-3
%  [arXiv:1605.04436 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4286-3;%%
  %30 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016pev}
%\bibitem{Khachatryan:2016pev} 
\item CMS Collaboration, ``Measurement of the differential cross section and charge asymmetry for inclusive $\mathrm {p}\mathrm {p}\rightarrow \mathrm {W}^{\pm }+X$ production at ${\sqrt{s}} = 8$ TeV'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 8, 469 (2016).
%  doi:10.1140/epjc/s10052-016-4293-4
%  [arXiv:1603.01803 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4293-4;%%
  %42 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016yro}
%\bibitem{Khachatryan:2016yro} 
\item CMS Collaboration, ``Measurement of the $ \mathrm{ Z } \gamma \rightarrow \nu \bar{\nu} \gamma$ production cross section in pp collisions at $\sqrt{s}=$ 8 TeV and limits on anomalous $ \mathrm{ ZZ } \gamma$ and $ \mathrm{Z} \gamma \gamma$ trilinear gauge boson couplings'', Phys.\ Lett.\ B {\bf 760}, 448 (2016).
%  doi:10.1016/j.physletb.2016.06.080
%  [arXiv:1602.07152 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2016.06.080;%%
  %11 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016hkr}
%\bibitem{Khachatryan:2016hkr} 
\item CMS Collaboration, ``Measurement of dijet azimuthal decorrelation in pp collisions at $\sqrt{s}=8\,\mathrm{TeV} $'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 10, 536 (2016).
%  doi:10.1140/epjc/s10052-016-4346-8
%  [arXiv:1602.04384 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4346-8;%%
  %11 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2016yte}
%\bibitem{Khachatryan:2016yte} 
\item CMS Collaboration, ``Forward–backward asymmetry of Drell–Yan lepton pairs in pp collisions at $\sqrt{s} = 8$ $\,\mathrm{TeV}$'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 6, 325 (2016).
%  doi:10.1140/epjc/s10052-016-4156-z
%  [arXiv:1601.04768 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4156-z;%%
  %16 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015luy}
%\bibitem{Khachatryan:2015luy} 
\item CMS Collaboration, ``Measurement of the inclusive jet cross section in pp collisions at $\sqrt{s} = 2.76\,\text {TeV}$'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 5, 265 (2016).
%  doi:10.1140/epjc/s10052-016-4083-z
%  [arXiv:1512.06212 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4083-z;%%
  %16 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015sga}
%\bibitem{Khachatryan:2015sga} 
\item CMS Collaboration, ``Measurement of the ${{\mathrm{W} }^{+} }\mathrm{W}^{-} $ cross section in pp collisions at $\sqrt{s} =$ 8 TeV and limits on anomalous gauge couplings'', Eur.\ Phys.\ J.\ C {\bf 76}, no. 7, 401 (2016).
%  doi:10.1140/epjc/s10052-016-4219-1
%  [arXiv:1507.03268 [hep-ex]].
  %%CITATION = doi:10.1140/epjc/s10052-016-4219-1;%%
  %60 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015ira}
%\bibitem{Khachatryan:2015ira} 
\item CMS Collaboration, ``Comparison of the Z/$\gamma$$^{∗}$ + jets to $\gamma$ + jets cross sections in pp collisions at $ \sqrt{s}=8 $ TeV'', JHEP {\bf 1510}, 128 (2015), Erratum: [JHEP {\bf 1604}, 010 (2016)].
%  doi:10.1007/JHEP04(2016)010, 10.1007/JHEP10(2015)128
%  [arXiv:1505.06520 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP04(2016)010, 10.1007/JHEP10(2015)128;%%
  %27 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015lba}
%\bibitem{Khachatryan:2015lba} 
\item CMS Collaboration, ``Search for a pseudoscalar boson decaying into a Z boson and the 125 GeV Higgs boson in $ℓ^+ℓ^−b\overline{b}$ final states'', Phys.\ Lett.\ B {\bf 748}, 221 (2015).
%  doi:10.1016/j.physletb.2015.07.010
%  [arXiv:1504.04710 [hep-ex]].
  %%CITATION = doi:10.1016/j.physletb.2015.07.010;%%
  %66 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015cwa}
%\bibitem{Khachatryan:2015cwa} 
\item CMS Collaboration, ``Search for a Higgs boson in the mass range from 145 to 1000 GeV decaying to a pair of W or Z bosons'', JHEP {\bf 1510}, 144 (2015).
%  doi:10.1007/JHEP10(2015)144
%  [arXiv:1504.00936 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP10(2015)144;%%
  %177 citations counted in INSPIRE as of 12 Jan 2018

%\cite{Khachatryan:2015bsa}
%\bibitem{Khachatryan:2015bsa} 
\item CMS Collaboration, ``Search for Third-Generation Scalar Leptoquarks in the t$\tau$ Channel in Proton-Proton Collisions at $\sqrt{s}$ = 8 TeV'', JHEP {\bf 1507}, 042 (2015), Erratum: [JHEP {\bf 1611}, 056 (2016)].
%  doi:10.1007/JHEP11(2016)056, 10.1007/JHEP07(2015)042
%  [arXiv:1503.09049 [hep-ex]].
  %%CITATION = doi:10.1007/JHEP11(2016)056, 10.1007/JHEP07(2015)042;%%
  %40 citations counted in INSPIRE as of 12 Jan 2018

\end{enumerate}

\fontsize{12pt}{12pt}\selectfont
