\begin{center}
{\large \bf{\em Acknowledgement}}
\end{center}
\vspace*{0.5cm}
{ \em
I would like to take this opportunity to thank the many people who helped make this dissertation possible.

In the first and foremost place, I gratefully express my sincere gratitude to my supervisor Prof.(Mrs.) Manjit Kaur for her invaluable assistance, support, guidance and blessings. She inspired me greatly to work in this project. Her willingness to motivate me contributed tremendously to this project. 

I am highly obliged to Prof. C.S. Aulakh Chairperson of the Department of Physics, Panjab University, Chandigarh, for his helping hand in providing a good environment and adequate facilities to complete this project successfully.

I feel deeply indebted to my parents for their unconditional love, understanding, support, strength, blessings and for everything.

I am greatly thankful to my well wishers, my friends Anu, Sohail, Junaid, Mandeep and my classmates for all that they meant to me during the crucial times of the completion of my project.

I owe my very special thanks to Mr. Inderpal Singh, Mrs. Prabhdeep Kaur, Mrs. Manuk Z. Mehta, Ms. Ritu Aggarwal, Ms. Ruchi Gupta, Ms. Monika Mittal and Ms. Genius, the members of high energy physics Laboratory, Dept. of Physics, P.U. for helping me out from all kinds of problems with their constant support, suggestions and encouragement. 

Finally and the most importantly, I would like to pay my greatest regards to the Almighty God for His blessings and kindness, a boundless and an endless source of inspiration for me always.} \\[2cm]
{November 15, 2012} \hspace*{8.cm}
{\em (Anterpreet Kaur)}
